### 2019-07-09 paper/paper.tex
Add JuliaCon Paper

% JuliaCon proceedings template
\documentclass{juliacon}
\setcounter{page}{1}

\usepackage{hyperref}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{graphicx}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{subcaption}
\usepackage{todonotes}

\setlength{\parindent}{2em}
\setlength{\parskip}{1em}

% Change link color
\hypersetup{colorlinks=true}

\begin{document}

\input{header}

\maketitle

\begin{abstract}
With the rising popularity of deep learning techniques, being able to differentiate through arbitrary functions is becoming more and more important. These arbitrary functions contain a lot of implicit knowledge stored in them which when used in combination with a neural network can significantly speed up its training. In this paper we present a fully differentiable renderer, which is designed to be integrated in any Differentiable Programming (DP) pipeline. We interface our renderer with the deep learning library Flux for use in combination with neural networks. We demonstrate the use of this differentiable renderer in complex rendering tasks and show its use in solving inverse graphics problems.

% \todo{Character count should not exceed 600}

\headingtable

\end{abstract}

% \let\thefootnote\relax\footnote{* Equal Contribution}

\section{Introduction}
\label{intro}

In Computer Graphics, a popular technique for rendering photo realistic images is raytracing. Since ray tracing leverages the properties of the materials of the objects in the scene, a natural extension to the rendering problem would be to extract the exact properties of the materials, lighting, etc. given an image of the scene. However, since ray tracing is non-differentiable at some points and calculating the analytic gradients is a very tedious task, it has been difficult to present a general inverse rendering method. As such there is only one framework in our knowledge, redner\cite{Li:2018:DMC}, which has been able to do so by using analytic gradients.

In this paper, we explore the idea of differentiability through a renderer, by leveraging the AD in Julia\cite{bezanson2017julia}. We present a fully general renderer capable of handling complex scenes and able to differentiate through them. We don't rely on analytic gradients but use source-to-source AD to generate efficient gradient code in the backward pass.

% IMAGES

\begin{figure*}[!htb]
    \centering
    \includegraphics[width=\textwidth]{images/performance-speed.png}
    \caption{Performance Gains on using BVH}
    \label{fig:bvh_perf}
\end{figure*}

\begin{figure*}[!htb]
    \centering
    \includegraphics[width=\textwidth]{images/performance-memory.png}
    \caption{Memory Allocation comparison between rendering with and without BVH}
    \label{fig:bvh_mem}
\end{figure*}

\begin{figure*}[!htb]
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/render/teapot_front.jpg}
        \caption*{}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/render/teapot_side.jpg}
        \caption*{}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/render/teapot_top.jpg}
        \caption*{}
    \end{subfigure}
    \caption{Utah Teapot Render from three different views. The camera definition shown in Listing~\protect[\ref{lst:example_render}] can be easily modified to generate all these views.}
    \label{fig:teapot_render}
\end{figure*}

\section{Background}
\label{sec:rendering}

Rendering is a technique of generating photorealistic or non photorealistic 2D projections from 3D objects. As such there are several algorithms for rendering complex scenes. One of the most popular techniques for photo realistic rendering is ray tracing. However, for real time rendering algorithms like rasterization is used.

Ray Tracing is a technique in computer graphics for rendering 3D graphics with complex light interactions. In this technique, rays are traced backwards from the eye/camera to the light source(s). In the path, the ray of light can undergo reflection and refraction due to interactions with the objects in its path. This method, however, is very computationally expensive and hence difficult to do in real time.

Rendering being a compute intensive operation is generally done in static languages like C++. This makes it very time expensive to develop the software. Also, these languages lack support of state of the art automatic differentiation tools like Zygote \cite{DBLP:journals/corr/abs-1810-07951}, Jax \cite{jax}, etc which are generally implemented for languages like Julia and Python. As such it is difficult to develop differentiable renderers in those languages and then interface with popular deep learning software.

\section{Differentiable Ray Tracing}

There are several photo-realistic renderers available which contain a vast amount of implicit knowledge. Differentiation allows such renderers to make use of gradients to learn the inverse mapping from an image to its parameter space. This knowledge can then be used in combination with any machine learning / deep learning model to train them in a fast and efficient manner.

However, as usual it is difficult to compute efficient derivatives from a production-ready renderer, typically written in a performance language like C++. This provides the primary motivation towards the development of RayTracer.jl. We develop an entire general purpose ray tracer in a high level numerical computation language. The presence of strong automatic differentiation libraries like Zygote.jl make it trivial to compute efficient derivatives from the renderer.

RayTracer.jl \cite{RayTracer.jl} is a package for Differentiable Ray Tracing written to solve this particular issue. It relies heavily on the source-to-source automatic differentiation package, Zygote for computing gradients with respect to arbitrary scene parameters. This package allows the user to configure the location of objects, lights and a camera in the scene. This scene is then interpreted by the renderer to generate the image. RayTracer.jl is naturally interfaced with the deep learning library Flux \cite{Flux.jl-2018}, due to the common AD backend, for use in more complex differentiable pipelines.

\section{Scene Rendering}

Our approach to differentiable rendering is based on first creating a general purpose renderer and then make use of efficient AD tools for the differentiability part. Hence, at its core RayTracer is a fully featured renderer. It contains functionalities for both raytracing and rasterization.

RayTracer gives users a lot of control to the user over the scene they want to render. The user controls the lighting in the scene, the shape and materials of the objects and the camera configuration. It might be worthwhile to note that we don't make any sort of performance compromise in the forward pass (rendering) to allow gradient computation.

\subsection{Accelerating the Rendering Process}

To accelerate the rendering process we have acceleration structures. Currently only one such acceleration structure, Bounding Volume Hierarchy \cite{Kay:1986:RTC:15922.15916}, is supported. We follow the exact same API for ray tracing using these accelerators. In this case instead of passing a \textit{Vector of Objects} we wrap it in a \textit{BoundingVolumeHierarchy} object and pass it. So in order to use this, we would have to change the scene variable to \textit{BoundingVolumeHierarchy(load\_obj("teapot.obj"))}.

We show the benefits of using Acceleration Structures in Figures~[\ref{fig:bvh_perf}] and [\ref{fig:bvh_mem}]. As can be seen from the plots we not only get a good performance gain (Figure~[\ref{fig:bvh_perf}]) in terms of speed, we also end up allocating much less memory (Figure~[\ref{fig:bvh_mem}] on using Bounding Volume Hierarchy.

\subsection{Rendering the Utah Teapot}

In this section we shall render a very popular model in computer graphics: the Utah Teapot. We simply load the model from a wavefront object (obj) file. Support for other types of files is trivial through the MeshIO.jl package with defines file reader for common mesh object files. Once the scene is loaded the next step is to configure the other elements in the scene - the camera and the light(s). Script~[\ref{lst:example_render}] illustrates the code for rendering the teapot model.

\begin{lstlisting}[caption = {Rendering the Utah Teapot Model},
                   label = {lst:example_render},
                   captionpos = b,
                   language = Julia]
# Screen Size
screen_size = (w = 512, h = 512)

# Camera Setup
cam = Camera(
    Vec3(1.0f0, 10.0f0, -1.0f0),
    Vec3(0.0f0),
    Vec3(0.0f0, 1.0f0, 0.0f0),
    45.0f0,
    1.0f0,
    screen_size...
)

origin, direction = get_primary_rays(cam)

# Scene
scene = load_obj("teapot.obj")

# Light Position
light = DistantLight(
    Vec3(1.0f0),
    100.0f0,
    Vec3(0.0f0, 1.0f0, 0.0f0)
)

# Render the image
color = raytrace(
    origin,
    direction,
    scene,
    light,
    origin,
    2
)
\end{lstlisting}

\section{Inverse Rendering}

Just like rendering can be thought of as the projection of 3D objects into a 2D plane, the inverse rendering problem can be described as just the opposite. It is the mapping of the 2D image back to the parameters of the scene.

As we have mentioned previously, one of the primary motivations of RayTracer.jl is for solving the problem of inverse graphics. Being able to compute gradients wrt any scene parameter, means that we can optimize that parameter. The optimization algorithm is pretty straight forward and is general enough to work for any arbitrary parameter. We describe the algorithm in [\ref{alg:inv_render}].

\begin{algorithm}[!htb]
    \caption{Gradient Based Optimization of Scene Parameters}
    \label{alg:inv_render}
    \SetAlgoLined
    \KwResult{Optimized set of Camera Parameters}
    Initial Guess of Parameters\;
    \While{not \textbf{converged} or iter < max\_iter}{
        gs = gradient(params) \textbf{do}\\
        ~~~~~~img = rendered image with params\;
        ~~~~~~loss = mean\_squared\_loss(img, target\_img)\;
        \textbf{end}\;
        \For{param in params}{
            update!(optimizer, param, gs[param])\;
        }
        \If{loss < tolerance}{
            converged = True\;
        }
    }
\end{algorithm}

% We shall provide two examples as a validation for our method. In both these experiments we have used Adam\cite{kingma2014adam} for optimization, but one can use any other method like L-BFGS, BFGS.

\section{Experiments}

\begin{figure*}[!htb]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/camera/initial_guess_image.png}
        \caption{Image with uncalibrated camera}
        \label{fig:cam_guess}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.23\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/camera/target_image.png}
        \caption{Target Image to be reconstructed}
        \label{fig:cam_target}
    \end{subfigure}
    \centering
    \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth, height=100px]{images/camera/iter_120.png}
        \caption{Image obtained after optimization}
    \end{subfigure}
    \caption{Calibration of Camera Parameters to reconstruct Image~[\ref{fig:cam_target}] from Image~[\ref{fig:cam_guess}]}
    \label{fig:cam_invrender}
\end{figure*}

\begin{figure*}[!htb]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\linewidth]{images/light/loss_plot_light.png}
        \caption{Loss Values over the Light Configuration Optimization Process}
        \label{fig:loss_plot_light}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \begin{subfigure}[b]{0.4\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/light/original.png}
            \caption{Image to be reconstructed}
            \label{fig:target_light}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.4\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/light/initial.png}
            \caption{Initial Guess of Lighting Parameters}
            \label{fig:guess_light}
        \end{subfigure}
        \centering
        \hfill
        \begin{subfigure}[b]{0.4\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/light/161.png}
            \caption{Image produced after 10 iterations}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.4\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/light/501.png}
            \caption{Image with converged parameters}
        \end{subfigure}
    \end{subfigure}
    \caption{Optimization of the lighting conditions to reconstruct Image~[\ref{fig:target_light}] from Image~[\ref{fig:guess_light}]}
    \label{fig:light_position}
\end{figure*}

In this section we showcase our differentiable renderer. Using the following two experiments we validate the functionality of the gradients of our renderer. In both the experiments we make use of the Adam optimizer as described in \cite{kingma2014adam}. We interface the raytracer with Flux to use these optimizers. As an alternative, we have tested the functioning of our package with the optimizers present in Optim.

\subsection{\textbf{Calibration of Camera Parameters}}

In this experiment we start with the image of a rectangle under some configuration of the Camera model. Our aim is to reconstruct the image of this rectangle by modifying the focus and the location of the camera. We assume that all the other parameters of the model, like the light configuration, position of objects, etc. are known apriori.

We follow the standard algorithm as defined in [\ref{alg:inv_render}] for optimizing the parameters. We make an initial guess of the parameters and initialize the camera as:

\begin{lstlisting}[language = Julia]
camera_guess =
    Camera(
        Vec3(5.0, -4.0, -20.0),
        Vec3(0.0, 0.0, 0.0),
        Vec3(0.0, 1.0, 0.0),
        90.0,
        3.0,
        screen_size...
    )
\end{lstlisting}

We use the mean squared difference between the rendered image and the target image as the loss and try to minimize that. The Adam optimizer is initialized with a learning rate of 0.05 and the model is declared to have as converged if the loss falls below 10. Figure~[\ref{fig:cam_invrender}] shows the optimization steps.

\subsection{\textbf{Optimizing the Light Source}}

In this experiment we describe our solution to the inverse lighting problem. In this case we assume the knowledge of the geometry and surface properties of the objects, camera position and the target image of the scene.

For this experiment we try to optimize the lighting for a scene containing a tree. We are given the target image with proper lighting conditions. We start with an arbitrary lighting and then iteratively improve the lighting using algorithm~[\ref{alg:inv_render}].

We present the images generated during the optimization process in Figure~[\ref{fig:light_position}].

\section{Conclusion}
In conclusion, we have presented how julia can be leveraged to build differentiable systems. Integrating them with the machine learning pipeline can make an end-to-end differentiable pipeline. Using this pipeline we can define differentiable programming algorithm on it to solve the problem. As expected making the pipeline differentiable allows us to exploit the huge amount of implicit knowledge stored in the system.

% \newpage

\bibliographystyle{juliacon}
\bibliography{ref}

\end{document}

% Inspired by the International Journal of Computer Applications template

### 2019-07-09 examples/script.sh

@@ -1,0 +1,31 @@
+#!/bin/bash
+
+# Set up the versions of packages
+julia --color=yes -e "using Pkg; Pkg.instantiate()"
+
+WORKDIR=$PWD
+
+# Teapot Rendering
+echo "Teapot Rendering Example"
+
+wget https://raw.githubusercontent.com/McNopper/OpenGL/master/Binaries/teapot.obj
+
+julia --project=. --color=yes "teapot_rendering.jl"
+
+# Performance Benchmarks
+
+echo "Performance Benchmarks"
+
+mkdir meshes
+cd meshes
+wget https://raw.githubusercontent.com/avik-pal/RayTracer.jl/ap/texture/test/meshes/sign_yield.obj
+wget https://raw.githubusercontent.com/avik-pal/RayTracer.jl/ap/texture/test/meshes/sign_yield.mtl1
+cd $WORKDIR
+
+mkdir textures
+cd textures
+wget https://raw.githubusercontent.com/avik-pal/RayTracer.jl/ap/texture/test/textures/wood_osb.jpg
+wget raw.githubusercontent.com/avik-pal/RayTracer.jl/ap/texture/test/textures/sign_yield.png
+cd $WORKDIR
+
+julia  --project=. --color=yes "performance_benchmarks.jl" -m "./meshes/sign_yield.jl" -g 2

### 2019-07-09 examples/teapot_rendering.jl

@@ -1,0 +1,51 @@
+using RayTracer, Images
+
+screen_size = (w = 128, h = 128)
+
+# Load the teapot object and ensure the type of the scene
+# vector is properly infered
+scene = load_obj("teapot.obj")
+
+# Define a convenience function for rendering and saving the images
+function generate_render_and_save(cam, light, filename)
+    # Get the primary rays for the camera
+    origin, direction = get_primary_rays(cam)
+
+    # Render the scene
+    color = raytrace(origin, direction, scene, light, origin, 2)
+
+    img = get_image(color, screen_size...)
+
+    save(filename, img)
+end
+
+# TOP VIEW Render
+# Setup the light position
+light = DistantLight(Vec3(1.0f0), 100.0f0, Vec3(0.0f0, 1.0f0, 0.0f0))
+
+# Setup the camera and generate the primary rays
+cam = Camera(Vec3(1.0f0, 10.0f0, -1.0f0), Vec3(0.0f0), Vec3(0.0f0, 1.0f0, 0.0f0),
+             45.0f0, 1.0f0, screen_size...)
+
+generate_render_and_save(cam, light, "teapot_top.jpg")
+
+# SIDE VIEW Render
+# Setup the light postion
+light = DistantLight(Vec3(1.0f0), 100.0f0, Vec3(1.0f0, 1.0f0, -1.0f0))
+
+# Camera setup
+cam = Camera(Vec3(1.0f0, 2.0f0, -10.0f0), Vec3(0.0f0, 1.0f0, 0.0f0),
+             Vec3(0.0f0, 1.0f0, 0.0f0), 45.0f0, 1.0f0, screen_size...)
+
+generate_render_and_save(cam, light, "teapot_side.jpg")
+
+# FRONT VIEW Render
+# Setup the light position
+light = DistantLight(Vec3(1.0f0), 100.0f0, Vec3(1.0f0, 1.0f0, 0.0f0))
+
+# Camera setup
+cam = Camera(Vec3(10.0f0, 2.0f0, 0.0f0), Vec3(0.0f0, 1.0f0, 0.0f0),
+             Vec3(0.0f0, 1.0f0, 0.0f0), 45.0f0, 1.0f0, screen_size...)
+
+generate_render_and_save(cam, light, "teapot_front.jpg")
+

### 2019-07-10 paper/paper.tex
Add numerical gradient checks

@@
 \begin{abstract}
-With the rising popularity of deep learning techniques, being able to differentiate through arbitrary functions is becoming more and more important.
-These arbitrary functions contain a lot of implicit knowledge stored in them which when used in combination with a neural network can significantly speed up its training.
-In this paper we present a fully differentiable renderer, which is designed to be integrated in any Differentiable Programming (DP) pipeline.
+In this paper we present RayTracer.jl, a renderer in Julia that is fully differentiable using source-to-source Automatic Differentiation (AD).
+This means that RayTracer not only renders 2D images from 3D scene parameters, but it can be used to optimize for model parameters that generate a target image in a Differentiable Programming (DP) pipeline.
 We interface our renderer with the deep learning library Flux for use in combination with neural networks.
-We demonstrate the use of this differentiable renderer in complex rendering tasks and show its use in solving inverse graphics problems.
-
-% \todo{Character count should not exceed 600}
+We demonstrate the use of this differentiable renderer in rendering tasks and in solving inverse graphics problems.
 
@@
 
-% \let\thefootnote\relax\footnote{* Equal Contribution}
-
-\section{Introduction}
-\label{intro}
-
-In Computer Graphics, a popular technique for rendering photo realistic images is raytracing.
-Since ray tracing leverages the properties of the materials of the objects in the scene, a natural extension to the rendering problem would be to extract the exact properties of the materials, lighting, etc.
-given an image of the scene.
-However, since ray tracing is non-differentiable at some points and calculating the analytic gradients is a very tedious task, it has been difficult to present a general inverse rendering method.
-As such there is only one framework in our knowledge, redner\cite{Li:2018:DMC}, which has been able to do so by using analytic gradients.
-
-In this paper, we explore the idea of differentiability through a renderer, by leveraging the AD in Julia\cite{bezanson2017julia}.
-We present a fully general renderer capable of handling complex scenes and able to differentiate through them.
-We don't rely on analytic gradients but use source-to-source AD to generate efficient gradient code in the backward pass.
-
 % IMAGES
@@
     \centering
-    \includegraphics[width=\textwidth]{images/performance-speed.png}
-    \caption{Performance Gains on using BVH}
+    \begin{subfigure}[c]{0.45\textwidth}
+        \includegraphics[height=75mm, width=\textwidth]{images/performance-speed.png}
+        \caption{Performance Benchmarks}
         \label{fig:bvh_perf}
-\end{figure*}
-
-\begin{figure*}[!htb]
-    \centering
-    \includegraphics[width=\textwidth]{images/performance-memory.png}
-    \caption{Memory Allocation comparison between rendering with and without BVH}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[c]{0.45\textwidth}
+        \includegraphics[height=75mm, width=\textwidth]{images/performance-memory.png}
+        \caption{Memory Allocation Benchmarks}
         \label{fig:bvh_mem}
+    \end{subfigure}
+    \caption{Comparison between scenes rendered with and without BVH}
+    \label{fig:bvh}
 \end{figure*}
@@
     \end{subfigure}
-    \caption{Utah Teapot Render from three different views. The camera definition shown in Listing~\protect[\ref{lst:example_render}] can be easily modified to generate all these views.}
+    \caption{Utah Teapot Render from three different views. The camera definition shown in Listing~\protect\ref{lst:example_render} can be easily modified to generate all these views.}
     \label{fig:teapot_render}
@@
 
-\section{Background}
-\label{sec:rendering}
+\section{Introduction}
+\label{intro}
 
@@
 One of the most popular techniques for photo realistic rendering is ray tracing.
-However, for real time rendering algorithms like rasterization is used.
+However, for real time rendering algorithms like rasterization are used.
 
@@
 In this technique, rays are traced backwards from the eye/camera to the light source(s).
-In the path, the ray of light can undergo reflection and refraction due to interactions with the objects in its path.
-This method, however, is very computationally expensive and hence difficult to do in real time.
+The ray of can undergo reflection and refraction due to interactions with the objects in its path.
+This technique, however, is very computationally expensive and hence difficult to do in real time.
+But since ray tracing leverages the properties of the materials of the objects in the scene, a natural extension to the rendering problem would be to extract the exact properties of the materials, lighting, etc.
+given an image of the scene.
+Unfortunately ray tracing is non-differentiable at some points and calculating the analytic gradients is a very tedious task.
+This has made it a very difficult task to present a general inverse rendering method.
+As such there is only one framework in our knowledge, redner\cite{Li:2018:DMC}, which has been able to do so by using analytic gradients.
 
-Rendering being a compute intensive operation is generally done in static languages like C++.
+Rendering being a computationally expensive operation is generally done in static languages like C++.
 This makes it very time expensive to develop the software.
-Also, these languages lack support of state of the art automatic differentiation tools like Zygote \cite{DBLP:journals/corr/abs-1810-07951}, Jax \cite{jax}, etc which are generally implemented for languages like Julia and Python.
+Also, most languages lack the support of state of the art automatic differentiation tools like Zygote \cite{DBLP:journals/corr/abs-1810-07951}, Jax \cite{jax}, etc which are generally implemented for high level languages like Julia and Python.
 As such it is difficult to develop differentiable renderers in those languages and then interface with popular deep learning software.
+
+In this paper, we explore the idea of differentiability through a renderer, by leveraging the AD in Julia\cite{bezanson2017julia}.
+We present a fully general renderer capable of handling complex scenes and able to differentiate through them.
+We don't rely on analytic gradients but use source-to-source AD to generate efficient gradient code in the backward pass.
 
@@
 Differentiation allows such renderers to make use of gradients to learn the inverse mapping from an image to its parameter space.
-This knowledge can then be used in combination with any machine learning / deep learning model to train them in a fast and efficient manner.
+This knowledge can then be used in combination with any machine learning / deep learning models to train them in a fast and efficient manner.
+Experiments in \cite{retinaface} demonstrate the effectiveness of incorporate differentiable renderers in deep learning pipelines by achieving State of the Art results in WIDERFace Hard dataset.
 
@@
 
+\todo[inline]{Add graphs comparing finite differencing to AD}
+
 \section{Scene Rendering}
@@
 It contains functionalities for both raytracing and rasterization.
+Additionally, unlike most prior work in differentiable rendering we do not make performance compromises in the forward pass (rendering) to allow gradient computation.
 
-RayTracer gives users a lot of control to the user over the scene they want to render.
-The user controls the lighting in the scene, the shape and materials of the objects and the camera configuration.
-It might be worthwhile to note that we don't make any sort of performance compromise in the forward pass (rendering) to allow gradient computation.
+RayTracer gives users a lot of control to the user over the scene they want to render. The user controls the lighting in the scene, the shape and materials of the objects and the camera configuration.
 
@@
 
-We show the benefits of using Acceleration Structures in Figures~[\ref{fig:bvh_perf}] and [\ref{fig:bvh_mem}].
-As can be seen from the plots we not only get a good performance gain (Figure~[\ref{fig:bvh_perf}]) in terms of speed, we also end up allocating much less memory (Figure~[\ref{fig:bvh_mem}] on using Bounding Volume Hierarchy.
+\todo[inline]{Clarifications and Reproducibility}
+We show the benefits of using Acceleration Structures in Figures~\ref{fig:bvh_perf} and \ref{fig:bvh_mem}.
+As can be seen from the plots we not only get a good performance gain (Figure~\ref{fig:bvh_perf}) in terms of speed, we also end up allocating much less memory (Figure~\ref{fig:bvh_mem} on using Bounding Volume Hierarchy.
 
 \subsection{Rendering the Utah Teapot}
+\todo[inline]{Clarity and Grammer}
 
@@
 Once the scene is loaded the next step is to configure the other elements in the scene - the camera and the light(s).
-Script~[\ref{lst:example_render}] illustrates the code for rendering the teapot model.
+Script~\ref{lst:example_render} illustrates the code for rendering the teapot model.
 
+\noindent
+\begin{minipage}{\linewidth}
 \begin{lstlisting}[caption = {Rendering the Utah Teapot Model},
@@
 \end{lstlisting}
+\end{minipage}
 
 \section{Inverse Rendering}
+
+\todo[inline]{More clarity in writing}
 
@@
 The optimization algorithm is pretty straight forward and is general enough to work for any arbitrary parameter.
-We describe the algorithm in [\ref{alg:inv_render}].
+We describe the algorithm in \ref{alg:inv_render}.
 
@@
 
-% We shall provide two examples as a validation for our method. In both these experiments we have used Adam\cite{kingma2014adam} for optimization, but one can use any other method like L-BFGS, BFGS.
-
 \section{Experiments}
@@
     \centering
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[c]{0.26\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{images/camera/initial_guess_image.png}
+        \includegraphics[width=107px, height=80px]{images/camera/initial_guess_image.png}
         \caption{Image with uncalibrated camera}
@@
     \hfill
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[c]{0.26\textwidth}
         \centering          
-        \includegraphics[width=\textwidth]{images/camera/target_image.png}
-        \caption{Target Image to be reconstructed}
+        \includegraphics[width=107px, height=80px]{images/camera/target_image.png}
+        \caption{Image to be reconstructed}
         \label{fig:cam_target}
@@
     \centering
-    \begin{subfigure}[b]{0.5\textwidth}
+    \begin{subfigure}[c]{0.47\textwidth}
         \centering
-        \includegraphics[width=\textwidth, height=100px]{images/camera/iter_120.png}
+        \includegraphics[width=\textwidth, height=80px]{images/camera/iter_120.png}
         \caption{Image obtained after optimization}
     \end{subfigure}
-    \caption{Calibration of Camera Parameters to reconstruct Image~[\ref{fig:cam_target}] from Image~[\ref{fig:cam_guess}]}
+    \caption{Calibration of Camera Parameters to reconstruct Image~\ref{fig:cam_target} from Image~\ref{fig:cam_guess}}
     \label{fig:cam_invrender}
@@
     \end{subfigure}
-    \caption{Optimization of the lighting conditions to reconstruct Image~[\ref{fig:target_light}] from Image~[\ref{fig:guess_light}]}
+    \caption{Optimization of the lighting conditions to reconstruct Image~\ref{fig:target_light} from Image~\ref{fig:guess_light}}
     \label{fig:light_position}
@@
 
-In this section we showcase our differentiable renderer.
-Using the following two experiments we validate the functionality of the gradients of our renderer.
+In this section we showcase our differentiable renderer in some toy inverse rendering problems.
+Using the following two experiments we demonstrate the use of gradients obtained via AD to recover the camera and lighting parameters fr a scene.
 In both the experiments we make use of the Adam optimizer as described in \cite{kingma2014adam}.
@@
 \subsection{\textbf{Calibration of Camera Parameters}}
+\label{sec:calcam}
 
-In this experiment we start with the image of a rectangle under some configuration of the Camera model.
-Our aim is to reconstruct the image of this rectangle by modifying the focus and the location of the camera.
-We assume that all the other parameters of the model, like the light configuration, position of objects, etc.
+In this experiment we start with the image of a rectangle (Listing~\ref{lst:rect_light}) under some configuration of the Camera model (Listing~\ref{lst:cam_opt}).
+Since RayTracer supports only two primitive shapes - Spheres and Triangles, we need to triangulate the rectangle.
+
+\noindent
+\begin{minipage}{\linewidth}
+\begin{lstlisting}[caption = {Configuration of the Rectangle for Experiment~\ref{sec:calcam}},
+                   label = {lst:rect_light},
+                   captionpos = b,
+                   language = Julia]
+scene = [
+    Triangle(
+        Vec3( 20.0,  10.0, 0.0),
+        Vec3( 20.0, -10.0, 0.0),
+        Vec3(-20.0,  10.0, 0.0),
+        Material(
+            color_diffuse = Vec3(0.0, 1.0, 0.0))),
+    Triangle(
+        Vec3(-20.0, -10.0, 0.0),
+        Vec3( 20.0, -10.0, 0.0),
+        Vec3(-20.0,  10.0, 0.0),
+        Material(
+            color_diffuse = Vec3(0.0, 1.0, 0.0)))
+]
+\end{lstlisting}
+\end{minipage}
+
+\noindent
+\begin{minipage}{\linewidth}
+\begin{lstlisting}[caption = {Camera Parameters to be Reconstructed},
+                   label = {lst:cam_opt},
+                   captionpos = b,
+                   language = Julia]
+camera_target =
+    Camera(
+        Vec3(0.0, 0.0, -30.0),
+        Vec3(0.0, 0.0,   0.0),
+        Vec3(0.0, 1.0,   0.0),
+        90.0,
+        1.0,
+        screen_size...
+    )
+\end{lstlisting}
+\end{minipage}
+
+\noindent
+\begin{minipage}{\linewidth}
+\begin{lstlisting}[caption = {Light Configuration},
+                   label = {lst:lgt_param},
+                   captionpos = b,
+                   language = Julia]
+light = PointLight(
+    Vec3(1.0, 0.0, 0.0),
+    100000.0,
+    Vec3(0.0, 0.0, -10.0)
+)
+\end{lstlisting}
+\end{minipage}
+
+Our aim is to reconstruct the image of this rectangle (Figure~\ref{fig:cam_target}) by modifying the focus and the location of the camera.
+We assume that all the other parameters of the model, like the light configuration (Listing~\ref{lst:lgt_param}), position of objects, etc.
 are known apriori.
+We use algorithm~\ref{alg:inv_render} for optimizing the parameters.
+We make an initial guess of the parameters and initialize the camera (Listing~\ref{lst:cam_initial}).
 
-We follow the standard algorithm as defined in [\ref{alg:inv_render}] for optimizing the parameters. We make an initial guess of the parameters and initialize the camera as:
-
-\begin{lstlisting}[language = Julia]
+\noindent
+\begin{minipage}{\linewidth}
+\begin{lstlisting}[caption = {Initial Guess of the Camera Parameters},
+                   label = {lst:cam_initial},
+                   captionpos = b,
+                   language = Julia]
 camera_guess =
@@
 \end{lstlisting}
+\end{minipage}
 
-We use the mean squared difference between the rendered image and the target image as the loss and try to minimize that.
-The Adam optimizer is initialized with a learning rate of 0.05 and the model is declared to have as converged if the loss falls below 10.
-Figure~[\ref{fig:cam_invrender}] shows the optimization steps.
+As our loss function, we use the mean squared difference between rendered and target images, each with $300\times400$ pixels having fractional RGB values.
+We minimize loss with the Adam optimizer, with learning rate 0.05, and declare the model to have converged if loss falls below 10 (where the initial loss is in the order of 600).
+Figure~\ref{fig:cam_invrender} shows the optimization steps.
 
 \subsection{\textbf{Optimizing the Light Source}}
+\todo[inline]{More details to reproduce the results}
 
@@
 We are given the target image with proper lighting conditions.
-We start with an arbitrary lighting and then iteratively improve the lighting using algorithm~[\ref{alg:inv_render}].
+We start with an arbitrary lighting and then iteratively improve the lighting using algorithm~\ref{alg:inv_render}.
 
-We present the images generated during the optimization process in Figure~[\ref{fig:light_position}].
+We present the images generated during the optimization process in Figure~\ref{fig:light_position}.
+
+\section{Current Limitations}
+\todo[inline]{Write this section highlighting the problem for non differentiable parts}
 
 \section{Conclusion}
+\todo[inline]{Needs a rewrite using the comments in the review}
 In conclusion, we have presented how julia can be leveraged to build differentiable systems.

### 2019-07-10 test/gradcheck.jl

@@ -13,23 +13,35 @@ end
 
 screen_size = (w = 400, h = 300)
 
-light = PointLight(Vec3(1.0f0), 1000.0f0, Vec3(0.15f0, 0.5f0, -110.5f0))
+light = PointLight(
+    Vec3(1.0),
+    1000.0,
+    Vec3(0.15, 0.5, -110.5)
+)
 
-eye_pos = Vec3(0.0f0, 0.0f0, -5.0f0)
+eye_pos = Vec3(0.0, 0.0, -5.0)
 
-cam = Camera(eye_pos, Vec3(0.0f0), Vec3(0.0f0, 1.0f0, 0.0f0), 45.0f0, 1.0f0, screen_size...)
+cam = Camera(eye_pos, Vec3(0.0), Vec3(0.0, 1.0, 0.0), 45.0, 1.0, screen_size...)
 
 origin, direction = get_primary_rays(cam);
 
 @testset "Triangle" begin
     scene = [
-        Triangle(Vec3(-1.7f0, 1.0f0, 0.0f0), Vec3(1.0f0, 1.0f0, 0.0f0), Vec3(1.0f0, -1.0f0, 0.0f0),
-                 Material())
+        Triangle(Vec3(-1.7, 1.0, 0.0), Vec3(1.0, 1.0, 0.0), Vec3(1.0, -1.0, 0.0),
+                 Material(color_ambient = Vec3(1.0),
+                          color_diffuse = Vec3(1.0),
+                          color_specular = Vec3(1.0),
+                          specular_exponent = 50.0,
+                          reflection = 1.0))
     ]
 
     scene_new = [
-        Triangle(Vec3(-1.9f0, 1.3f0, 0.1f0), Vec3(1.2f0, 1.1f0, 0.3f0), Vec3(0.8f0, -1.2f0, -0.15f0),
-                 Material())
+        Triangle(Vec3(-1.9, 1.3, 0.1), Vec3(1.2, 1.1, 0.3), Vec3(0.8, -1.2, -0.15),
+                 Material(color_ambient = Vec3(1.0),
+                          color_diffuse = Vec3(1.0),
+                          color_specular = Vec3(1.0),
+                          specular_exponent = 50.0,
+                          reflection = 1.0))
     ]
     
     color = raytrace(origin, direction, scene, light, eye_pos, 0)
@@ -38,17 +50,16 @@ origin, direction = get_primary_rays(cam);
 
[…]

### 2019-07-11 paper/paper.tex
Update the paper and the toml files

@@
 The presence of strong automatic differentiation libraries like Zygote.jl make it trivial to compute efficient derivatives from the renderer.
+We present the performance gains we get on using Zygote as compared to Central Differencing in Figure~\ref{fig:ad_perf}.
+
+\begin{figure}[!htb]
+    \centering
+    \includegraphics[width=\linewidth, height=150px]{images/differentiation.png}
+    \caption{Performance Comparison between Zygote AD and Numerical Differentiation}
+    \label{fig:ad_perf}
+\end{figure}
 
@@
 RayTracer.jl is naturally interfaced with the deep learning library Flux \cite{Flux.jl-2018}, due to the common AD backend, for use in more complex differentiable pipelines.
-
-\todo[inline]{Add graphs comparing finite differencing to AD}
 

### 2019-07-11 src/optimize.jl

@@ -37,7 +37,7 @@ update!(opt, x::T, Δ::T) where {T<:Real} = (update!(opt, [x], [Δ]))[]
 # This makes sure we donot end up optimizing the value of the material.
 # We cannot do this update in a stable manner for now. So it is wise
 # to just avoid it for now.
-update!(opt, x::Material, Δ::Material) = x
+# update!(opt, x::Material, Δ::Material) = x
 
 update!(opt, x::FixedParams, Δ::FixedParams) = x 
 

### 2019-07-11 test/gradcheck.jl

@@ -55,11 +55,21 @@ end
     
 @testset "Sphere" begin
     scene = [
-        Sphere(Vec3(-1.7, 1.0, 0.0), [0.6], Material())
+        Sphere(Vec3(-1.7, 1.0, 0.0), [0.6],
+               Material(color_ambient = Vec3(1.0),
+                        color_diffuse = Vec3(1.0),
+                        color_specular = Vec3(1.0),
+                        specular_exponent = 50.0,
+                        reflection = 1.0))
     ]
 
     scene_new = [
-        Sphere(Vec3(-1.9, 1.3, 0.1), [0.9], Material())
+        Sphere(Vec3(-1.9, 1.3, 0.1), [0.9],
+	       Material(color_ambient = Vec3(1.0),
+                        color_diffuse = Vec3(1.0),
+                        color_specular = Vec3(1.0),
+                        specular_exponent = 50.0,
+                        reflection = 1.0))
     ]
     
     color = raytrace(origin, direction, scene, light, eye_pos, 0)

### 2019-07-11 paper/paper.tex
Update paper as per review

@@
 \begin{abstract}
-In this paper we present RayTracer.jl, a renderer in Julia that is fully differentiable using source-to-source Automatic Differentiation (AD).
+In this paper, we present RayTracer.jl, a renderer in Julia that is fully differentiable using source-to-source Automatic Differentiation (AD).
 This means that RayTracer not only renders 2D images from 3D scene parameters, but it can be used to optimize for model parameters that generate a target image in a Differentiable Programming (DP) pipeline.
@@
 
-Rendering is a technique of generating photorealistic or non photorealistic 2D projections from 3D objects.
+Rendering is a technique of generating photorealistic or non-photorealistic 2D projections from 3D objects.
 As such there are several algorithms for rendering complex scenes.
-One of the most popular techniques for photo realistic rendering is ray tracing.
-However, for real time rendering algorithms like rasterization are used.
+One of the most popular techniques for photorealistic rendering is ray tracing.
+However, for real-time rendering algorithms like rasterization is used.
 
 Ray Tracing is a technique in computer graphics for rendering 3D graphics with complex light interactions.
-In this technique, rays are traced backwards from the eye/camera to the light source(s).
-The ray of can undergo reflection and refraction due to interactions with the objects in its path.
-This technique, however, is very computationally expensive and hence difficult to do in real time.
+In this technique, rays are traced backward from the eye/camera to the light source(s).
+The ray can undergo reflection and refraction due to interactions with the objects in its path.
+This technique, however, is very computationally expensive and hence difficult to do in real-time.
 But since ray tracing leverages the properties of the materials of the objects in the scene, a natural extension to the rendering problem would be to extract the exact properties of the materials, lighting, etc.
 given an image of the scene.
-Unfortunately ray tracing is non-differentiable at some points and calculating the analytic gradients is a very tedious task.
+Unfortunately, ray tracing is non-differentiable at some points and calculating the analytic gradients is a very tedious task.
 This has made it a very difficult task to present a general inverse rendering method.
-As such there is only one framework in our knowledge, redner\cite{Li:2018:DMC}, which has been able to do so by using analytic gradients.
+As such, there is only one framework in our knowledge, redner\cite{Li:2018:DMC}, which has been able to do so by using analytic gradients.
 
-Rendering being a computationally expensive operation is generally done in static languages like C++.
+Rendering is a computationally expensive technique, and so it is generally done in static languages like C++.
 This makes it very time expensive to develop the software.
-Also, most languages lack the support of state of the art automatic differentiation tools like Zygote \cite{DBLP:journals/corr/abs-1810-07951}, Jax \cite{jax}, etc which are generally implemented for high level languages like Julia and Python.
-As such it is difficult to develop differentiable renderers in those languages and then interface with popular deep learning software.
+Also, most languages lack the support of the state of the art automatic differentiation tools like Zygote \cite{DBLP:journals/corr/abs-1810-07951}, Jax \cite{jax}, etc which are generally implemented for high-level languages like Julia and Python.
+As such, it is difficult to develop differentiable renderers in those languages and then interface with popular deep learning software.
 
@@
 Differentiation allows such renderers to make use of gradients to learn the inverse mapping from an image to its parameter space.
-This knowledge can then be used in combination with any machine learning / deep learning models to train them in a fast and efficient manner.
+We can then use this knowledge in combination with any machine learning / deep learning models to train them in a fast and efficient manner.
 Experiments in \cite{retinaface} demonstrate the effectiveness of incorporate differentiable renderers in deep learning pipelines by achieving State of the Art results in WIDERFace Hard dataset.
 
-However, as usual it is difficult to compute efficient derivatives from a production-ready renderer, typically written in a performance language like C++.
+However, as usual, it is difficult to compute efficient derivatives from a production-ready renderer, typically written in a performance language like C++.
 This provides the primary motivation towards the development of RayTracer.jl.
-We develop an entire general purpose ray tracer in a high level numerical computation language.
+We develop an entire general purpose ray tracer in a high-level numerical computation language.
 The presence of strong automatic differentiation libraries like Zygote.jl make it trivial to compute efficient derivatives from the renderer.
@@
 
-To accelerate the rendering process we have acceleration structures.
-Currently only one such acceleration structure, Bounding Volume Hierarchy \cite{Kay:1986:RTC:15922.15916}, is supported.
+To accelerate the rendering process we support an acceleration structure, Bounding Volume Hierarchy \cite{Kay:1986:RTC:15922.15916}.
 We follow the exact same API for ray tracing using these accelerators.
@@
 
-\todo[inline]{Clarifications and Reproducibility}
-We show the benefits of using Acceleration Structures in Figures~\ref{fig:bvh_perf} and \ref{fig:bvh_mem}.
-As can be seen from the plots we not only get a good performance gain (Figure~\ref{fig:bvh_perf}) in terms of speed, we also end up allocating much less memory (Figure~\ref{fig:bvh_mem} on using Bounding Volume Hierarchy.
+Using acceleration structures allow us to minimize the total allocations (Figure~\ref{fig:bvh_mem}) and gives us a significant performance boost (Figure~\ref{fig:bvh_perf}).
+For these measurements we use a mesh with $137$ centered at the origin\footnote{We provide the code for reproducing the experiment in \href{https://github.com/avik-pal/RayTracer.jl/examples}{https://github.com/avik-pal/RayTracer.jl/examples}}.
 
 \subsection{Rendering the Utah Teapot}
-\todo[inline]{Clarity and Grammer}
 
-In this section we shall render a very popular model in computer graphics: the Utah Teapot.
-We simply load the model from a wavefront object (obj) file.
-Support for other types of files is trivial through the MeshIO.jl package with defines file reader for common mesh object files.
-Once the scene is loaded the next step is to configure the other elements in the scene - the camera and the light(s).
-Script~\ref{lst:example_render} illustrates the code for rendering the teapot model.
+In this section we demonstrate the general pipeline for defining a 3D scene using RayTracer.jl and then rendering it.
+We are going to render the popular Utah Teapot model.
+We need to specify the 3D model in the form of a Vector of Objects.
+We can do it manually for custom scenes or we could simply load it from a wavefront object (obj) file.
+Support for additional file formats can be provided via MeshIO.jl.
+Apart from the scene vector, we need to specify the camera configuration and the configuration of light(s).
+We summarize the entire code to render the teapot in Listing~\ref{lst:example_render}.
 
-\noindent
-\begin{minipage}{\linewidth}
+% \noindent
+% \begin{minipage}{\linewidth}
 \begin{lstlisting}[caption = {Rendering the Utah Teapot Model},
@@
 \end{lstlisting}
-\end{minipage}
+% \end{minipage}
 
@@
 
-\todo[inline]{More clarity in writing}
+The rendering problem is to project 3D scene parameters to form an image in the 2D plane.
+Inverse Rendering problem is just the opposite: generating a mapping from the 2D image back to the parameters of the 3D scene.
 
-Just like rendering can be thought of as the projection of 3D objects into a 2D plane, the inverse rendering problem can be described as just the opposite.
-It is the mapping of the 2D image back to the parameters of the scene.
-
-As we have mentioned previously, one of the primary motivations of RayTracer.jl is for solving the problem of inverse graphics.
-Being able to compute gradients wrt any scene parameter, means that we can optimize that parameter.
-The optimization algorithm is pretty straight forward and is general enough to work for any arbitrary parameter.
-We describe the algorithm in \ref{alg:inv_render}.
+One of the primary motivations of RayTracer.jl is to solve the inverse graphics problem.
+Since the renderer can be used to compute the gradient with respect to any arbitrary parameter (as long as it is differentiable), we can then use any gradient based optimization technique to optimize on that parameter.
+This allows us to propose a generalized Algorithm~\ref{alg:inv_render} which is capable of optimizing any differentiable parameter.
 
@@
 
-\begin{figure*}[!htb]
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\linewidth]{images/light/loss_plot_light.png}
-        \caption{Loss Values over the Light Configuration Optimization Process}
-        \label{fig:loss_plot_light}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.45\textwidth}
-        \begin{subfigure}[b]{0.4\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{images/light/original.png}
-            \caption{Image to be reconstructed}
-            \label{fig:target_light}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.4\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{images/light/initial.png}
-            \caption{Initial Guess of Lighting Parameters}
-            \label{fig:guess_light}
-        \end{subfigure}
-        \centering
-        \hfill
-        \begin{subfigure}[b]{0.4\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{images/light/161.png}
-            \caption{Image produced after 10 iterations}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.4\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{images/light/501.png}
-            \caption{Image with converged parameters}
-        \end{subfigure}
-    \end{subfigure}
-    \caption{Optimization of the lighting conditions to reconstruct Image~\ref{fig:target_light} from Image~\ref{fig:guess_light}}
-    \label{fig:light_position}
-\end{figure*}
-
 In this section we showcase our differentiable renderer in some toy inverse rendering problems.
-Using the following two experiments we demonstrate the use of gradients obtained via AD to recover the camera and lighting parameters fr a scene.
+Using the following two experiments we demonstrate the use of gradients obtained via AD to recover the camera, material and lighting parameters for a scene.
 In both the experiments we make use of the Adam optimizer as described in \cite{kingma2014adam}.
@@
 
-\subsection{\textbf{Calibration of Camera Parameters}}
+\subsection{Calibration of Camera Parameters}
 \label{sec:calcam}
 
-In this experiment we start with the image of a rectangle (Listing~\ref{lst:rect_light}) under some configuration of the Camera model (Listing~\ref{lst:cam_opt}).
+In this experiment we start with the image of a rectangle (Listing~\ref{lst:light_config}) under some configuration of the Camera model (Listing~\ref{lst:cam_opt}).
 Since RayTracer supports only two primitive shapes - Spheres and Triangles, we need to triangulate the rectangle.
 
-\noindent
-\begin{minipage}{\linewidth}
-\begin{lstlisting}[caption = {Configuration of the Rectangle for Experiment~\ref{sec:calcam}},
-                   label = {lst:rect_light},
+% \noindent
+% \begin{minipage}{\linewidth}
+\begin{lstlisting}[caption = {Configuration of the Scene for Experiment~\ref{sec:calcam}},
+                   label = {lst:light_config},
                    captionpos = b,
@@
 ]
+
+light = PointLight(
+    Vec3(1.0, 0.0, 0.0),
+    100000.0,
+    Vec3(0.0, 0.0, -10.0)
+)
 \end{lstlisting}
-\end{minipage}
+% \end{minipage}
 
@@
 \begin{minipage}{\linewidth}
-\begin{lstlisting}[caption = {Light Configuration},
-                   label = {lst:lgt_param},
-                   captionpos = b,
-                   language = Julia]
-light = PointLight(
-    Vec3(1.0, 0.0, 0.0),
-    100000.0,
-    Vec3(0.0, 0.0, -10.0)
-)
-\end{lstlisting}
-\end{minipage}
-
-Our aim is to reconstruct the image of this rectangle (Figure~\ref{fig:cam_target}) by modifying the focus and the location of the camera.
-We assume that all the other parameters of the model, like the light configuration (Listing~\ref{lst:lgt_param}), position of objects, etc.
-are known apriori.
-We use algorithm~\ref{alg:inv_render} for optimizing the parameters.
-We make an initial guess of the parameters and initialize the camera (Listing~\ref{lst:cam_initial}).
-
-\noindent
-\begin{minipage}{\linewidth}
 \begin{lstlisting}[caption = {Initial Guess of the Camera Parameters},
@@
 
+Our aim is to reconstruct the image of this rectangle (Figure~\ref{fig:cam_target}) by modifying the focus and the location of the camera.
+We assume that all the other parameters of the model, like the light configuration (Listing~\ref{lst:light_config}), position of objects, etc.
+are known apriori.
+We use algorithm~\ref{alg:inv_render} for optimizing the parameters.
+We make an initial guess of the parameters and initialize the camera (Listing~\ref{lst:cam_initial}).
+
 As our loss function, we use the mean squared difference between rendered and target images, each with $300\times400$ pixels having fractional RGB values.
@@
 
-\subsection{\textbf{Optimizing the Light Source}}
-\todo[inline]{More details to reproduce the results}
+\subsection{Optimizing the Light Source}
+\label{sec:light_source}
+
+\begin{figure*}[!htb]
+    \centering
+    \begin{subfigure}[c]{0.45\textwidth}
+        \includegraphics[width=\linewidth]{images/light/loss_plot_light.png}
+        \caption{Loss Values over the Light Configuration Optimization Process}
+        \label{fig:loss_plot_light}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[c]{0.45\textwidth}
+        \begin{subfigure}[c]{0.45\textwidth}
+            \centering
+            \includegraphics[width=\textwidth]{images/light/original.png}
+            \caption{Image to be reconstructed}
+            \label{fig:target_light}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[c]{0.45\textwidth}
+            \centering
+            \includegraphics[width=\textwidth]{images/light/initial.png}
+            \caption{Initial Guess of Lighting Parameters}
+            \label{fig:guess_light}
+        \end{subfigure}
+        \centering
+        \hfill
+        \begin{subfigure}[c]{0.45\textwidth}
+            \centering
+            \includegraphics[width=\textwidth]{images/light/161.png}
+            \caption{Image produced after 10 iterations}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[c]{0.45\textwidth}
+            \centering
+            \includegraphics[width=\textwidth]{images/light/501.png}
+            \caption{Image with converged parameters}
+        \end{subfigure}
+    \end{subfigure}
+    \caption{Optimization of the lighting conditions to reconstruct Image~\ref{fig:target_light} from Image~\ref{fig:guess_light}}
+    \label{fig:light_position}
+\end{figure*}
 
 In this experiment we describe our solution to the inverse lighting problem.
-In this case we assume the knowledge of the geometry and surface properties of the objects, camera position and the target image of the scene.
+This problem involved predicting the configuration of the light source(s) in the scene given a target image (Figure~\ref{fig:target_light}).
+All the other information about the geometry and surface properties of the objects and the camera configuration are already known.
+Listing~\ref{lst:initial_config_expt2} describes the known configurations.
 
-For this experiment we try to optimize the lighting for a scene containing a tree.
-We are given the target image with proper lighting conditions.
-We start with an arbitrary lighting and then iteratively improve the lighting using algorithm~\ref{alg:inv_render}.
+\noindent
+\begin{minipage}{\linewidth}
+\begin{lstlisting}[caption = {Configuration of the Scene for Experiment~\ref{sec:light_source}},
+                   label = {lst:initial_config_expt2},
+                   captionpos = b,
+                   language = Julia]
 
-We present the images generated during the optimization process in Figure~\ref{fig:light_position}.
+screen_size = (w = 128, h = 128)
+
+camera = Camera(
+    Vec3(0.0f0, 6.0f0, -10.0f0),
+    Vec3(0.0f0, 2.0f0,  0.0f0),
+    Vec3(0.0f0, 1.0f0,  0.0f0),
+    45.0f0,
+    0.5f0,
+    screen_size...
+)
+
+scene = load_obj("tree.obj")
+\end{lstlisting}
+\end{minipage}
+
+The object in our scene is a tree.
+We start with an arbitrary lighting (Listing~\ref{lst:lgt_guess}) condition and then iteratively improve the lighting using Algorithm~\ref{alg:inv_render}.
+We present the loss curve and the images generated during the optimization process in Figure~\ref{fig:light_position}.
+
+\noindent
+\begin{minipage}{\linewidth}
+\begin{lstlisting}[caption = {Target Lighting Conditions},
+                   label = {lst:lgt_target},
+                   captionpos = b,
+                   language = Julia]
+light_target = PointLight(
+    Vec3(1.0f0, 1.0f0, 1.0f0),
+    20000.0f0,
+    Vec3(1.0f0, 10.0f0, -50.0f0)
+)
+\end{lstlisting}
+\end{minipage}
+
+\noindent
+\begin{minipage}{\linewidth}
+\begin{lstlisting}[caption = {Initial Guess of Lighting Conditions},
+                   label = {lst:lgt_guess},
+                   captionpos = b,
+                   language = Julia]
+light_guess = PointLight(
+    Vec3(1.0f0, 1.0f0, 1.0f0),
+    10000.0f0,
+    Vec3(-1.0f0, -10.0f0, -50.0f0)
+)
+\end{lstlisting}
+\end{minipage}
+
+\subsection{Retrieving Color of Materials}
+\label{sec:mat_color}
+
+\begin{figure}[!htb]
+    \centering
+    \begin{subfigure}[c]{0.23\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{images/material/target.png}
+        \caption{Image to be reconstructed}
+        \label{fig:target_material}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[c]{0.23\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{images/material/initial.png}
+        \caption{Initial Guess of the Materials}
+        \label{fig:guess_material}
+    \end{subfigure}
+    \centering
+    \hfill
+    \begin{subfigure}[c]{0.23\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{images/material/1.png}
+        \caption{Image produced after just 1 iteration}
+        \label{fig:single_step}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[c]{0.23\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{images/material/33.png}
+        \caption{Image obtained after 35 iterations}
+    \end{subfigure}
+    \caption{Optimization of the materials of the mesh to reconstruct Image~\ref{fig:target_material} from Image~\ref{fig:guess_material}}
+    \label{fig:mat_correction}
+\end{figure}
+
+RayTracer.jl can also be used to recover the properties of the material of a mesh.
+For this experiment we shall use the same tree mesh from Experiment~\ref{sec:light_source}.
+We are going to optimize the diffuse color of the mesh.
+The position of the camera and the lighting conditions are mentioned in Listing~\ref{lst:config_mat}.
+
+The major difference of this optimization from the prior experiments is that the range of values the color can take is constrained between $0.0$ and $1.0$.
+Hence, after every step of the optimizer we need to clamp the value of the diffuse color for each mesh triangle.
+
+We use the sum squared loss function.
+We minimize the loss with Adam optimizer, with a learning rate of 0.05.
+The converge of the model is quite fast and we get a good approximation of the paramters just after a single optimizer step (Figure~\ref{fig:single_step}).
+
+\noindent
+\begin{minipage}{\linewidth}
+\begin{lstlisting}[caption = {Configuration of the Scene for Experiment~\ref{sec:mat_color}},
+                   label = {lst:config_mat},
+                   captionpos = b,
+                   language = Julia]
+screen_size = (w = 400, h = 300)
+
+light = PointLight(
+    Vec3(1.0f0),
+    1000000.0f0,
+    Vec3(0.15f0, 0.5f0, -10.5f0)
+)
+
+cam = Camera(
+    Vec3(-2.0f0, 2.0f0, -5.0f0),
+    Vec3( 0.0f0, 1.7f0,  0.0f0),
+    Vec3( 0.0f0, 1.0f0,  0.0f0),
+    45.0f0,
+    1.0f0,
+    screen_size...
+)
+
+scene = load_obj("tree.obj")
+\end{lstlisting}
+\end{minipage}
 
 \section{Current Limitations}
-\todo[inline]{Write this section highlighting the problem for non differentiable parts}
+
+Despite the success of our approach in solving a variety of inverse graphics problems, we fail to deal with problems that are non-differentiable in nature.
+One such instance would be estimating the proper geometry of an object given an image.
+Such problems are non-differentiable due to the large number of discrete choices in the position of the triangle vertices.
+Hence, trying to optimize such parameters generally causes them to diverge.
+The other cases which we can't handle properly are secondary lighting (shadows) and global illumination.
+Most of these cases can be dealt with, similar to the way proposed by \cite{Li:2018:DMC}, but that leads to a significant slowdown to the rendering of the scene.
 
 \section{Conclusion}
-\todo[inline]{Needs a rewrite using the comments in the review}
-In conclusion, we have presented how julia can be leveraged to build differentiable systems.
-Integrating them with the machine learning pipeline can make an end-to-end differentiable pipeline.
-Using this pipeline we can define differentiable programming algorithm on it to solve the problem.
-As expected making the pipeline differentiable allows us to exploit the huge amount of implicit knowledge stored in the system.
 
-% \newpage
+In conclusion, we have showed how Julia can be leveraged to build differentiable systems.
+We have presented which to the best of our knowledge is the first differentiable renderer which uses source-to-source AD.
+We have used a set of toy examples to demonstrate the ability of our renderer to reconstruct scenes (which are differentiable) from only a single image.
+This also shows that this renderer can be used in differentiable programming pipelines which involve image generation.
 

### 2019-07-17 paper/paper.tex

@@
 This has made it a very difficult task to present a general inverse rendering method.
-As such, there is only one framework in our knowledge, redner\cite{Li:2018:DMC}, which has been able to do so by using analytic gradients.
+As such, there is only one framework in our knowledge, redner~\cite{Li:2018:DMC}, which has been able to do so by using analytic gradients.
 
@@
 This makes it very time expensive to develop the software.
-Also, most languages lack the support of the state of the art automatic differentiation tools like Zygote \cite{DBLP:journals/corr/abs-1810-07951}, Jax \cite{jax}, etc which are generally implemented for high-level languages like Julia and Python.
+Also, most languages lack the support of the state of the art automatic differentiation tools like Zygote~\cite{DBLP:journals/corr/abs-1810-07951}, Jax~\cite{jax}, etc., which are generally implemented for high-level languages like Julia and Python.
 As such, it is difficult to develop differentiable renderers in those languages and then interface with popular deep learning software.
 
-In this paper, we explore the idea of differentiability through a renderer, by leveraging the AD in Julia\cite{bezanson2017julia}.
+In this paper, we explore the idea of differentiability through a renderer, by leveraging the AD in Julia~\cite{bezanson2017julia}.
 We present a fully general renderer capable of handling complex scenes and able to differentiate through them.
@@
 We can then use this knowledge in combination with any machine learning / deep learning models to train them in a fast and efficient manner.
-Experiments in \cite{retinaface} demonstrate the effectiveness of incorporate differentiable renderers in deep learning pipelines by achieving State of the Art results in WIDERFace Hard dataset.
+Experiments in~\cite{retinaface} demonstrate the effectiveness of incorporate differentiable renderers in deep learning pipelines by achieving State of the Art results in WIDERFace Hard dataset.
 
@@
 
-RayTracer.jl \cite{RayTracer.jl} is a package for Differentiable Ray Tracing written to solve this particular issue.
-It relies heavily on the source-to-source automatic differentiation package, Zygote for computing gradients with respect to arbitrary scene parameters.
+RayTracer.jl~\cite{RayTracer.jl} is a package for Differentiable Ray Tracing written to solve this particular issue.
+It relies heavily on the source-to-source automatic differentiation package Zygote for computing gradients with respect to arbitrary scene parameters.
 This package allows the user to configure the location of objects, lights and a camera in the scene.

### 2019-07-17 paper/paper.tex
Update paper.tex

@@
 Using the following two experiments we demonstrate the use of gradients obtained via AD to recover the camera, material and lighting parameters for a scene.
-In both the experiments we make use of the Adam optimizer as described in \cite{kingma2014adam}.
+In both experiments we make use of the Adam optimizer as described in~\cite{kingma2014adam}.
 We interface the raytracer with Flux to use these optimizers.
@@
 In this experiment we start with the image of a rectangle (Listing~\ref{lst:light_config}) under some configuration of the Camera model (Listing~\ref{lst:cam_opt}).
-Since RayTracer supports only two primitive shapes - Spheres and Triangles, we need to triangulate the rectangle.
+Since RayTracer supports only two primitive shapes, Spheres and Triangles, we need to triangulate the rectangle.
 
@@
 We minimize the loss with Adam optimizer, with a learning rate of 0.05.
-The converge of the model is quite fast and we get a good approximation of the paramters just after a single optimizer step (Figure~\ref{fig:single_step}).
+The convergence of the model is quite fast and we get a good approximation of the paramters just after a single optimizer step (Figure~\ref{fig:single_step}).
 

### 2019-07-18 docs/make.jl
Add a better tutorial for rendering

@@ -8,8 +8,7 @@ makedocs(modules=[RayTracer],
                                   assets = ["assets/documenter.css"]),
          pages = ["Home" => "index.md",
                   "Getting Started" => [
-                      "Rendering" => "getting_started/rendering.md",
-                      "Inverse Rendering" => "getting_started/optimization.md"],
+                      "Introduction to Rendering" => "getting_started/teapot_rendering.md"],
                   "API Documentation" => "api.md"])
 
 deploydocs(repo = "github.com/avik-pal/RayTracer.jl.git")

### 2019-07-18 examples/teapot_rendering.jl

@@ -1,51 +1,152 @@
+# # Introduction to rendering using RayTracer.jl
+#
+# In this example we will render the famous UTAH Teapot model.
+# We will go through the entire rendering API. We will load
+# an obj file for the scene. This needs to be downloaded manually.
+#
+# Run this code in your terminal to get the file:
+# `wget https://raw.githubusercontent.com/McNopper/OpenGL/master/Binaries/teapot.obj`
+
 using RayTracer, Images
 
-screen_size = (w = 128, h = 128)
+# ## General Attributes of the Scene
+#
+# Specify the dimensions of the image we want to generate.
+# `screen_size` is never passed into the RayTracer directly so it
+# need not be a named tuple.
+screen_size = (w = 256, h = 256)
 
-# Load the teapot object and ensure the type of the scene
-# vector is properly infered
+# Load the teapot object from an `obj` file. We can also specify
+# the scene using primitive objects directly but that becomes a
+# bit involved when there are complicated objects in the scene.
 scene = load_obj("teapot.obj")
 
-# Define a convenience function for rendering and saving the images
+# We shall define a convenience function for rendering and saving
+# the images
 function generate_render_and_save(cam, light, filename)
-    # Get the primary rays for the camera
+    #src # Get the primary rays for the camera
     origin, direction = get_primary_rays(cam)
 
-    # Render the scene
+    #src # Render the scene
     color = raytrace(origin, direction, scene, light, origin, 2)
 
+    #src # This will reshape `color` into the proper dimensions and return
+    #src # an RGB image
     img = get_image(color, screen_size...)
 
+    #src # Display the image
+    display(img)
+
+    #src # Save the generated image
     save(filename, img)
 end
 
-# TOP VIEW Render
-# Setup the light position
-light = DistantLight(Vec3(1.0f0), 100.0f0, Vec3(0.0f0, 1.0f0, 0.0f0))
+# ## Understanding the `Light` and `Camera` API
+#
+# ### DistantLight
+#
[…]

### 2019-07-18 docs/make.jl
Add a detailed documentation

@@ -1,14 +1,28 @@
 using Documenter, RayTracer
 
-makedocs(modules=[RayTracer],
-         doctest = false,
-         sitename = "RayTracer",
-         authors = "Avik Pal",
-         format = Documenter.HTML(prettyurls = true,
-                                  assets = ["assets/documenter.css"]),
-         pages = ["Home" => "index.md",
-                  "Getting Started" => [
-                      "Introduction to Rendering" => "getting_started/teapot_rendering.md"],
-                  "API Documentation" => "api.md"])
+makedocs(
+    modules = [RayTracer],
+    doctest = true,
+    sitename = "RayTracer",
+    authors = "Avik Pal",
+    format = Documenter.HTML(
+        prettyurls = get(ENV, "CI", nothing) == "true",
+    ),
+    pages = [
+        "Home"              => "index.md",
+        "Getting Started"   => [
+            "Introduction to Rendering" => "getting_started/teapot_rendering.md",
+        ],
+        "API Documentation" => [
+            "General Utilities"   => "api/utilities.md",
+            "Differentiation"     => "api/differentiation.md",
+            "Scene Configuration" => "api/scene.md",
+            "Renderers"           => "api/renderers.md",
+            "Optimization"        => "api/optimization.md",
+        ],
+    ],
+)
 
-deploydocs(repo = "github.com/avik-pal/RayTracer.jl.git")
+deploydocs(
+    repo = "github.com/avik-pal/RayTracer.jl.git"
+)

### 2019-07-18 examples/teapot_rendering.jl

@@ -22,7 +22,10 @@ screen_size = (w = 256, h = 256)
 scene = load_obj("teapot.obj")
 
 # We shall define a convenience function for rendering and saving
-# the images
+# the images.
+# For understanding the parameters passed to the individual functions
+# look into the documentations of [`get_primary_rays`](@ref), [`raytrace`](@ref)
+# and [`get_image`](@ref)
 function generate_render_and_save(cam, light, filename)
     #src # Get the primary rays for the camera
     origin, direction = get_primary_rays(cam)
@@ -45,7 +48,7 @@ end
 #
 # ### DistantLight
 #
-# In this example we will be using the `DistantLight`. This king of lighting
+# In this example we will be using the [`DistantLight`](@ref). This king of lighting
 # is useful when we want to render a scene in which all parts of the scene
 # receive the same intensity of light.
 # 
@@ -56,8 +59,9 @@ end
 #
 # ### Camera
 #
-# We use a perspective view Camera Model in RayTracer. Let us look into the
+# We use a perspective view [`Camera`](@ref) Model in RayTracer. Let us look into the
 # arguments we need to pass into the Camera constructor.
+#
 # * LookFrom - The position of the Camera
 # * LookAt   - The point in 3D space where the Camera is pointing
 # * vup      - The UP vector of the world (typically Vec3(0.0, 1.0, 0.0), i.e. the y-axis)

### 2019-07-18 src/camera.jl

@@ -4,6 +4,18 @@ export Camera, get_primary_rays
 # Camera #
 # ------ #
 
+"""
+    FixedCameraParams
+
+The Parameters of the [`Camera`](@ref) which should not be updated in inverse rendering
+are wrapped into this object.
+
+### Fields:
+
+* `vup`    - Stores the World UP Vector (In most cases this is the Y-Axis Vec3(0.0, 1.0, 0.0))
+* `width`  - Width of the image to be rendered
+* `height` - Height of the image to be rendered
+"""
 struct FixedCameraParams{T} <: FixedParams
     vup::Vec3{T}
     width::Int
@@ -17,6 +29,27 @@ Base.show(io::IO, fcp::FixedCameraParams) =
 Base.zero(fcp::FixedCameraParams) = FixedCameraParams(zero(fcp.vup), zero(fcp.width),
                                                       zero(fcp.height))
 
+"""
+    Camera
+
+The Perspective View Camera Model
+
+### Fields:
+
+* `lookfrom`    - Position of the Camera in 3D World Space
+* `lookat`      - Point in the 3D World Space where the Camera is Pointing
+* `vfov`        - Field of View of the Camera
+* `focus`       - The focal length of the Camera
+* `fixedparams` - An instance of [`FixedCameraParams`](@ref)
+
+### Available Constructors:
+
+* `Camera(;lookfrom = Vec3(0.0f0), lookat = Vec3(0.0f0),
+           vup = Vec3(0.0f0, 1.0f0, 0.0f0), vfov = 90.0f0,
+           focus = 1.0f0, width = 128, height = 128)`
+* `Camera(lookfrom::Vec3{T}, lookat::Vec3{T}, vup::Vec3{T}, vfov::R,
+          focus::R, width::Int, height::Int) where {T<:AbstractArray, R<:Real}` 
+"""
 struct Camera{T}
     lookfrom::Vec3{T}
     lookat::Vec3{T}
@@ -32,6 +65,11 @@ Base.show(io::IO, cam::Camera) =
                                        
 @diffops Camera
 
+Camera(;lookfrom = Vec3(0.0f0), lookat = Vec3(0.0f0),
+        vup = Vec3(0.0f0, 1.0f0, 0.0f0), vfov = 90.0f0,
+        focus = 1.0f0, width = 128, height = 128) =
+    Camera(lookfrom, lookat, vup, vfov, focus, width, height)
+
[…]

### 2019-07-18 src/gradients/numerical.jl

@@ -39,6 +39,43 @@ end
 
 Get the parameters from a struct that can be tuned. The output is in
 the form of an array.
+
+### Example:
+
+```jldoctest
+julia> using RayTracer;
+
+julia> scene = Triangle(Vec3(-1.9f0, 1.6f0, 1.0f0), Vec3(1.0f0, 1.0f0, 0.0f0), Vec3(-0.5f0, -1.0f0, 0.0f0),
+                        Material())
+Triangle Object:
+    Vertex 1 - x = -1.9, y = 1.6, z = 1.0
+    Vertex 2 - x = 1.0, y = 1.0, z = 0.0
+    Vertex 3 - x = -0.5, y = -1.0, z = 0.0
+    Material{Array{Float32,1},Array{Float32,1},Nothing,Nothing,Nothing,Nothing}(x = 1.0, y = 1.0, z = 1.0, x = 1.0, y = 1.0, z = 1.0, x = 1.0, y = 1.0, z = 1.0, Float32[50.0], Float32[0.5], nothing, nothing, nothing, nothing)
+
+julia> RayTracer.get_params(scene)
+20-element Array{Float32,1}:
+ -1.9
+  1.6
+  1.0
+  1.0
+  1.0
+  0.0
+ -0.5
+ -1.0
+  0.0
+  1.0
+  1.0
+  1.0
+  1.0
+  1.0
+  1.0
+  1.0
+  1.0
+  1.0
+ 50.0
+  0.5
+```
 """
 get_params(x::T, typehelp = Float32) where {T<:AbstractArray} = x
 
@@ -57,25 +94,50 @@ Sets the tunable parameters of the struct `x`. The index of the last element
 set into the struct is returned as output. This may be used to confirm that
 the size of the input array was as expected.
 
-### Example
+### Example:
 
-```julia
-julia> scene = Triangle(Vec3(-1.9, 1.3, 0.1), Vec3(1.2, 1.1, 0.3), Vec3(0.8, -1.2, -0.15),
-                    color = rgb(1.0, 1.0, 1.0), reflection = 0.5)
[…]

### 2019-07-18 src/imutils.jl

@@ -11,6 +11,13 @@ using Zygote: @adjoint
 
 Reshapes and normalizes a Vec3 color format to the RGB format of Images
 for easy loading, saving and visualization.
+
+### Arguments:
+
+* `image`  - The rendered image in flattened Vec3 format
+           (i.e., the output of the raytrace, rasterize, etc.)
+* `width`  - Width of the output image
+* `height` - Height of the output image
 """
 function get_image(im::Vec3{T}, width, height) where {T}
     low = eltype(T)(0)
@@ -28,5 +35,10 @@ end
     zeroonenorm(x::AbstractArray)
 
 Normalizes the elements of the array to values between `0` and `1`.
+
+!!! note
+    This function exists because the version of Zygote we use returns
+    incorrect gradient for `1/maximum(x)` function. This has been fixed
+    on the latest release of Zygote.
 """
 zeroonenorm(x) = (x .- minimum(x)) ./ (maximum(x) - minimum(x))

### 2019-07-18 src/objects/obj_parser.jl

@@ -3,7 +3,16 @@ export load_obj
 # ------------------------- #
 # - Parse OBJ & MTL Files - #
 # ------------------------- #
+"""
+    triangulate_faces(vertices::Vector, texture_coordinates::Vector,
+                      faces::Vector, material_map::Dict)
 
+Triangulates the `faces` and converts it into valid [`Triangle`](@ref) objects.
+
+!!! warning
+    Avoid using this function in itself. It is designed to be used internally
+    by the [`load_obj`](@ref) function.
+"""
 function triangulate_faces(vertices::Vector, texture_coordinates::Vector,
                            faces::Vector, material_map::Dict)
     scene = Vector{Triangle}()
@@ -39,6 +48,16 @@ function triangulate_faces(vertices::Vector, texture_coordinates::Vector,
     end
 end
 
+"""
+    parse_mtllib!(file, material_map, outtype)
+
+Parses `.mtl` file and creates a map from the material name to 
+[`Material`](@ref) objects.
+
+Not all fields of the `mtl` file are parsed. We only parse :
+`newmtl`, `Ka`, `Kd`, `Ks`, `Ns`, `d`, `Tr`, `map_Kd`, `map_Ks`,
+and `map_Ka`.
+"""
 function parse_mtllib!(file, material_map, outtype)
     color_diffuse = Vec3(outtype(1.0f0))
     color_ambient = Vec3(outtype(1.0f0))
@@ -122,6 +141,14 @@ function parse_mtllib!(file, material_map, outtype)
     return nothing
 end
 
+"""
+    load_obj(file; outtype = Float32)
+
+Parser for `obj` file. It returns a set of Triangles that make up the scene.
+
+Only the following things are parsed as of now: `v`, `vt`, `vn`, `f`, `usemtl`
+and `mtllib`.
+"""
 function load_obj(file; outtype = Float32)
     vertices = Vector{Vec3{Vector{outtype}}}()
     texture_coordinates = Vector{Tuple}()

### 2019-07-18 src/objects/triangle.jl

@@ -4,6 +4,19 @@ export Triangle
 # - Triangle - #
 # ------------ #
 
+"""
+    Triangle
+
+Triangle is a primitive object. Any complex object can be represented as a mesh
+of Triangles.
+
+### Fields:
+
+* `v1`       - Vertex 1
+* `v2`       - Vertex 2
+* `v3`       - Vertex 3
+* `material` - Material of the Triangle
+"""
 struct Triangle{V, P, Q, R, S, T, U} <: Object
     v1::Vec3{V}
     v2::Vec3{V}

### 2019-07-18 src/optimize.jl

@@ -20,11 +20,11 @@ type conversion of `x` which can significantly slow doen the raytracer.
 ### Example:
 
 ```julia
-opt = ADAM()
+julia> opt = ADAM()
 
-gs = gradient(loss_function, θ)
+julia> gs = gradient(loss_function, θ)
 
-update!(opt, θ, gs[1])
+julia> update!(opt, θ, gs[1])
 ```
 """
 function update!(opt, x::AbstractArray, Δ::AbstractArray)
@@ -33,11 +33,6 @@ function update!(opt, x::AbstractArray, Δ::AbstractArray)
 end
 
 update!(opt, x::T, Δ::T) where {T<:Real} = (update!(opt, [x], [Δ]))[]
-
-# This makes sure we donot end up optimizing the value of the material.
-# We cannot do this update in a stable manner for now. So it is wise
-# to just avoid it for now.
-# update!(opt, x::Material, Δ::Material) = x
 
 update!(opt, x::FixedParams, Δ::FixedParams) = x 
 

### 2019-07-18 docs/make.jl
Added documentation for BVH and raytrace

@@ -14,11 +14,12 @@ makedocs(
             "Introduction to Rendering" => "getting_started/teapot_rendering.md",
         ],
         "API Documentation" => [
-            "General Utilities"   => "api/utilities.md",
-            "Differentiation"     => "api/differentiation.md",
-            "Scene Configuration" => "api/scene.md",
-            "Renderers"           => "api/renderers.md",
-            "Optimization"        => "api/optimization.md",
+            "General Utilities"         => "api/utilities.md",
+            "Differentiation"           => "api/differentiation.md",
+            "Scene Configuration"       => "api/scene.md",
+            "Renderers"                 => "api/renderers.md",
+            "Optimization"              => "api/optimization.md",
+            "Acceleration Structures"   => "api/accelerators.md",
         ],
     ],
 )

### 2019-07-18 src/bvh.jl

@@ -1,7 +1,33 @@
 export BoundingVolumeHierarchy
 
+"""
+    AccelerationStructure
+
+Base Type for all Acceleration Structures. These can be used to speed up
+rendering by a significant amount. The main design behind an acceleration
+structure should be such that it can be used as a simple replacement for
+a vector of [`Object`](@ref)s.
+"""                  
 abstract type AccelerationStructure end
 
+"""
+    BVHNode
+
+A node in the graph created from the scene list using [`BoundingVolumeHierarchy`](@ref).
+
+### Fields:
+
+* `x_min`       - Minimum x-value for the bounding box
+* `x_max`       - Maximum x-value for the bounding box
+* `y_min`       - Minimum y-value for the bounding box 
+* `y_max`       - Maximum y-value for the bounding box 
+* `z_min`       - Minimum z-value for the bounding box 
+* `z_max`       - Maximum z-value for the bounding box 
+* `index_start` - Starting triangle in the scene list
+* `index_end`   - Last triangle in the scene list
+* `left_child`  - Can be `nothing` or another [`BVHNode`](@ref)
+* `right_child` - Can be `nothing` or another [`BVHNode`](@ref)
+"""
 struct BVHNode{T}
     x_min::T
     x_max::T
@@ -15,6 +41,18 @@ struct BVHNode{T}
     right_child::Union{Nothing, BVHNode}
 end
 
+"""
+    BoundingVolumeHierarchy
+
+Construct the Bounding Volume Hierarchy from a given Vector of
+[`Triangle`](@ref)s.
+
+### Fields:
+
+* `scene_list` - The scene list passed into the BVH constructor but in
+                 sorted order
+* `root_node`  - Root [`BVHNode`](@ref)
+"""
 struct BoundingVolumeHierarchy{T, S} <: AccelerationStructure
     scene_list::Vector{T}
     root_node::BVHNode{S}

### 2019-07-18 src/renderers/blinnphong.jl

@@ -11,6 +11,10 @@ Implements the Blinn Phong rendering algorithm. This function is merely for
 internal usage and should in no case be called by the user. This function is
 quite general and supports user defined **Objects**. For support of custom
 Objects have a look at the examples.
+
+!!! warning
+    Don't try to use this function by itself. But if you are person who likes
+    to ignore warnings look into the way [`raytrace`](@ref) calls this.
 """
 function light(s::Object, origin, direction, dist, lgt::Light, eye_pos,
                scene, obj_num, bounce)
@@ -46,8 +50,14 @@ function light(s::Object, origin, direction, dist, lgt::Light, eye_pos,
 end
 
 """
-    raytrace(origin::Vec3, direction::Vec3, scene::Vector, lgt::Light, eye_pos::Vec3, bounce::Int)
-    raytrace(origin::Vec3, direction::Vec3, scene::Vector, lgt::Vector{Light}, eye_pos::Vec3, bounce::Int)
+    raytrace(origin::Vec3, direction::Vec3, scene::Vector, lgt::Light,
+             eye_pos::Vec3, bounce::Int)
+    raytrace(origin::Vec3, direction::Vec3, scene, lgt::Vector{Light},
+             eye_pos::Vec3, bounce::Int)
+    raytrace(origin::Vec3, direction::Vec3, scene::BoundingVolumeHierarchy,
+             lgt::Light, eye_pos::Vec3, bounce::Int)
+    raytrace(;origin = nothing, direction = nothing, scene = nothing,
+              light_source = nothing, global_illumination = false)
 
 Computes the color contribution to every pixel by tracing every single ray.
 Internally it calls the `light` function which implements Blinn Phong Rendering
@@ -65,7 +75,15 @@ much faster if global illumination is off but at the same time is much less phot
     The support for multiple lights is primitive as we loop over the lights.
     Even though it is done in a parallel fashion, it is not the best way to
     do so. Nevertheless it exists just for the sake of experimentation.
+
+!!! note
+    None of the parameters (except global_illumination) in the keyword argument version of
+    [`raytrace`](@ref) is optional. It is just present for convenience.
 """
+raytrace(;origin = nothing, direction = nothing, scene = nothing,
+          light_source = nothing, global_illumination = false) =
+    raytrace(origin, direction, scene, light_source, origin, global_illumination ? 0 : 2)
+
[…]

### 2019-07-19 src/renderers/blinnphong.jl
Final documentation additions

@@ -13,7 +13,7 @@ quite general and supports user defined **Objects**. For support of custom
 Objects have a look at the examples.
 
 !!! warning
-    Don't try to use this function by itself. But if you are person who likes
+    Don't try to use this function by itself. But if you are a person who likes
     to ignore warnings look into the way [`raytrace`](@ref) calls this.
 """
 function light(s::Object, origin, direction, dist, lgt::Light, eye_pos,

### 2019-07-19 docs/make.jl
Improve the documentation css and README

@@ -7,6 +7,7 @@ makedocs(
     authors = "Avik Pal",
     format = Documenter.HTML(
         prettyurls = get(ENV, "CI", nothing) == "true",
+        assets     = ["assets/raytracer.css"],
     ),
     pages = [
         "Home"              => "index.md",

### 2019-07-19 examples/inverse_lighting.jl

@@ -1,0 +1,10 @@
+# # Inverse Lighting Tutorial
+#
+# In this tutorial we shall explore the inverse lighting problem.
+# Here, we shall try to reconstruct a target image by optimizing
+# the parameters of the light source (using gradients).
+
+using RayTracer, Images, Zygote, Flux, Statistics
+
+# Reduce the screen_size if the optimization is taking a bit long
+screen_size = (w = 300, h = 300)

### 2019-07-19 docs/make.jl
Add inverse rendering tutorial

@@ -13,6 +13,7 @@ makedocs(
         "Home"              => "index.md",
         "Getting Started"   => [
             "Introduction to Rendering" => "getting_started/teapot_rendering.md",
+            "Inverse Lighting"          => "getting_started/inverse_lighting.md",
         ],
         "API Documentation" => [
             "General Utilities"         => "api/utilities.md",

### 2019-07-19 examples/inverse_lighting.jl

@@ -6,5 +6,118 @@
 
 using RayTracer, Images, Zygote, Flux, Statistics
 
+# ## Configuring the Scene
+#
 # Reduce the screen_size if the optimization is taking a bit long
 screen_size = (w = 300, h = 300)
+
+# Now we shall load the scene using [`load_obj`](@ref) function. For
+# this we need the `obj` and `mtl` files. This will be downloaded using
+# the following commands:
+#
+# ```
+# wget https://raw.githubusercontent.com/tejank10/Duckietown.jl/master/src/meshes/tree.obj
+# wget https://raw.githubusercontent.com/tejank10/Duckietown.jl/master/src/meshes/tree.mtl
+# ```
+scene = load_obj("./tree.obj")
+
+# Let us set up the [`Camera`](@ref). For a more detailed understanding of
+# the rendering process look into [Introduction to rendering using RayTracer.jl](@ref).
+cam = Camera(
+    Vec3(0.0f0, 6.0f0, -10.0f0),
+    Vec3(0.0f0, 2.0f0,  0.0f0),
+    Vec3(0.0f0, 1.0f0,  0.0f0),
+    45.0f0,
+    0.5f0,
+    screen_size...
+)
+
+origin, direction = get_primary_rays(cam)
+
+# We should define a few convenience functions. Since we are going to calculate
+# the gradients only wrt to `light` we have it as an argument to the function. Having
+# `scene` as an additional parameters simply allows us to test our method for other
+# meshes without having to run `Zygote.refresh()` repeatedly.
+function render(light, scene)
+    packed_image = raytrace(origin, direction, scene, light, origin, 2)
+    array_image = reshape(hcat(packed_image.x, packed_image.y, packed_image.z),
+                          (screen_size.w, screen_size.h, 3, 1))
+    return array_image
+end
+
+showimg(img) = colorview(RGB, permutedims(img[:,:,:,1], (3,2,1)))
+
+# ## Ground Truth Image
+#
+# For this tutorial we shall use the [`PointLight`](@ref) source.
+# We define the ground truth lighting source and the rendered image. We
+# will later assume that we have no information about this lighting
+# condition and try to reconstruct the image.
+light_gt = PointLight(
+    Vec3(1.0f0, 1.0f0, 1.0f0),
+    20000.0f0,
+    Vec3(1.0f0, 10.0f0, -50.0f0)
+)
+
+target_img = render(light_gt, scene)
+
[…]

### 2019-07-19 examples/script.sh

@@ -19,7 +19,7 @@ echo "Performance Benchmarks"
 mkdir meshes
 cd meshes
 wget https://raw.githubusercontent.com/avik-pal/RayTracer.jl/ap/texture/test/meshes/sign_yield.obj
-wget https://raw.githubusercontent.com/avik-pal/RayTracer.jl/ap/texture/test/meshes/sign_yield.mtl1
+wget https://raw.githubusercontent.com/avik-pal/RayTracer.jl/ap/texture/test/meshes/sign_yield.mtl
 cd $WORKDIR
 
 mkdir textures

### 2019-07-19 examples/teapot_rendering.jl

@@ -7,7 +7,8 @@
 # Run this code in your terminal to get the file:
 # `wget https://raw.githubusercontent.com/McNopper/OpenGL/master/Binaries/teapot.obj`
 
-using RayTracer, Images
+# If you are using REPL mode you need the `ImageView.jl` package
+using RayTracer, Images #, ImageView
 
 # ## General Attributes of the Scene
 #
@@ -38,13 +39,14 @@ function generate_render_and_save(cam, light, filename)
     img = get_image(color, screen_size...)
 
     #src # Display the image
+    #src # For REPL mode change this to `imshow(img)`
     display(img)
 
     #src # Save the generated image
     save(filename, img)
 end
 
-# ## Understanding the `Light` and `Camera` API
+# ## Understanding the [`Light`](@ref) and [`Camera`](@ref) API
 #
 # ### DistantLight
 #

### 2019-07-19 paper/paper.tex
Add usage example with Optim

--- 2019-07-17 paper/paper.tex
@@
     Vec3(1.0f0, 1.0f0, 1.0f0),
-    10000.0f0,
+    1.0f0,
     Vec3(-1.0f0, -10.0f0, -50.0f0)

### 2019-07-19 docs/make.jl

@@ -6,7 +6,7 @@ makedocs(
     sitename = "RayTracer",
     authors = "Avik Pal",
     format = Documenter.HTML(
-        prettyurls = get(ENV, "CI", nothing) == "true",
+        # prettyurls = get(ENV, "CI", nothing) == "true",
         assets     = ["assets/raytracer.css"],
     ),
     pages = [
@@ -14,6 +14,7 @@ makedocs(
         "Getting Started"   => [
             "Introduction to Rendering" => "getting_started/teapot_rendering.md",
             "Inverse Lighting"          => "getting_started/inverse_lighting.md",
+            "Optimizing using Optim.jl" => "getting_started/optim_compatibility.md",
         ],
         "API Documentation" => [
             "General Utilities"         => "api/utilities.md",

### 2019-07-19 examples/inverse_lighting.jl

@@ -47,7 +47,7 @@ end
 
 showimg(img) = colorview(RGB, permutedims(img[:,:,:,1], (3,2,1)))
 
-# ## Ground Truth Image
+# ## [Ground Truth Image](@id inv_light)
 #
 # For this tutorial we shall use the [`PointLight`](@ref) source.
 # We define the ground truth lighting source and the rendered image. We
@@ -72,7 +72,7 @@ showimg(zeroonenorm(render(light_gt, scene)))
 # ## Initial Guess of Lighting Parameters
 #
 # We shall make some arbitrary guess of the lighting parameters (intensity and 
-# position) and try to get back the image in [Ground Truth Image](@ref)
+# position) and try to get back the image in [Ground Truth Image](@ref inv_light)
 light_guess = PointLight(
     Vec3(1.0f0, 1.0f0, 1.0f0),
     1.0f0,

### 2019-07-19 examples/optim_compatibility.jl

@@ -1,0 +1,153 @@
+# # Optimizing Scene Parameters using Optim.jl
+#
+# In this tutorial we will explore the exact same problem as demonstrated
+# in [Inverse Lighting Tutorial](@ref) but this time we will use the
+# Optimization Package [Optim.jl](https://julianlsolvers.github.io/Optim.jl/stable/).
+# I would recommend going through a few of the
+# [tutorials on Optim](https://julianlsolvers.github.io/Optim.jl/stable/#user/minimization/#_top)
+# before starting this one.
+#
+# If you have already read the previous tutorial, you can safely skip to
+# [Writing the Optimization Loop using Optim](@ref). The part previous to this
+# is same as the previous tutorial.
+
+using RayTracer, Images, Zygote, Flux, Statistics, Optim
+
+# ## Configuring the Scene
+#
+# If you want a better quality image increase this value but it will slow down the
+# optimization.
+screen_size = (w = 64, h = 64)
+
+# Now we shall load the scene using [`load_obj`](@ref) function. For
+# this we need the `obj` and `mtl` files. This will be downloaded using
+# the following commands:
+#
+# ```
+# wget https://raw.githubusercontent.com/tejank10/Duckietown.jl/master/src/meshes/tree.obj
+# wget https://raw.githubusercontent.com/tejank10/Duckietown.jl/master/src/meshes/tree.mtl
+# ```
+scene = load_obj("./tree.obj")
+
+# Let us set up the [`Camera`](@ref). For a more detailed understanding of
+# the rendering process look into [Introduction to rendering using RayTracer.jl](@ref).
+cam = Camera(
+    Vec3(0.0f0, 6.0f0, -10.0f0),
+    Vec3(0.0f0, 2.0f0,  0.0f0),
+    Vec3(0.0f0, 1.0f0,  0.0f0),
+    45.0f0,
+    0.5f0,
+    screen_size...
+)
+
+origin, direction = get_primary_rays(cam)
+
+# We should define a few convenience functions. Since we are going to calculate
+# the gradients only wrt to `light` we have it as an argument to the function. Having
+# `scene` as an additional parameters simply allows us to test our method for other
+# meshes without having to run `Zygote.refresh()` repeatedly.
+function render(light, scene)
+    packed_image = raytrace(origin, direction, scene, light, origin, 2)
+    array_image = reshape(hcat(packed_image.x, packed_image.y, packed_image.z),
[…]

### 2019-07-19 examples/script.sh

@@ -28,4 +28,17 @@ wget https://raw.githubusercontent.com/avik-pal/RayTracer.jl/ap/texture/test/tex
 wget raw.githubusercontent.com/avik-pal/RayTracer.jl/ap/texture/test/textures/sign_yield.png
 cd $WORKDIR
 
-julia  --project=. --color=yes "performance_benchmarks.jl" -m "./meshes/sign_yield.jl" -g 2
+julia --project=. --color=yes "performance_benchmarks.jl" -m "./meshes/sign_yield.jl" -g 2
+
+# Inverse Lighting
+
+echo "Inverse Lighting"
+
+cd meshes
+wget https://raw.githubusercontent.com/tejank10/Duckietown.jl/master/src/meshes/tree.obj
+wget https://raw.githubusercontent.com/tejank10/Duckietown.jl/master/src/meshes/tree.mtl
+cd $WORKDIR
+
+julia --project=. --color=yes "inverse_lighting.jl"
+julia --project=. --color=yes "optim_compatibility.jl"
+

### 2019-07-19 examples/teapot_rendering.jl

@@ -46,7 +46,7 @@ function generate_render_and_save(cam, light, filename)
     save(filename, img)
 end
 
-# ## Understanding the [`Light`](@ref) and [`Camera`](@ref) API
+# ## Understanding the Light and Camera API
 #
 # ### DistantLight
 #

### 2019-07-19 docs/make.jl
Typo in README path

@@ -6,7 +6,7 @@ makedocs(
     sitename = "RayTracer",
     authors = "Avik Pal",
     format = Documenter.HTML(
-        # prettyurls = get(ENV, "CI", nothing) == "true",
+        prettyurls = get(ENV, "CI", nothing) == "true",
         assets     = ["assets/raytracer.css"],
     ),
     pages = [

### 2019-07-20 examples/inverse_lighting.jl
Changes suggested in code review

@@ -12,8 +12,9 @@ using RayTracer, Images, Zygote, Flux, Statistics
 screen_size = (w = 300, h = 300)
 
 # Now we shall load the scene using [`load_obj`](@ref) function. For
-# this we need the `obj` and `mtl` files. This will be downloaded using
-# the following commands:
+# this we need the [`obj`](https://en.wikipedia.org/wiki/Wavefront_.obj_file)
+# and [`mtl`](https://en.wikipedia.org/wiki/Wavefront_.obj_file#Material_template_library)
+# files. They can be downloaded using the following commands:
 #
 # ```
 # wget https://raw.githubusercontent.com/tejank10/Duckietown.jl/master/src/meshes/tree.obj
@@ -24,12 +25,13 @@ scene = load_obj("./tree.obj")
 # Let us set up the [`Camera`](@ref). For a more detailed understanding of
 # the rendering process look into [Introduction to rendering using RayTracer.jl](@ref).
 cam = Camera(
-    Vec3(0.0f0, 6.0f0, -10.0f0),
-    Vec3(0.0f0, 2.0f0,  0.0f0),
-    Vec3(0.0f0, 1.0f0,  0.0f0),
-    45.0f0,
-    0.5f0,
-    screen_size...
+    lookfrom = Vec3(0.0f0, 6.0f0, -10.0f0),
+    lookat   = Vec3(0.0f0, 2.0f0,  0.0f0),
+    vup      = Vec3(0.0f0, 1.0f0,  0.0f0),
+    vfov     = 45.0f0,
+    focus    = 0.5f0,
+    width    = screen_size.w,
+    height   = screen_size.h
 )
 
 origin, direction = get_primary_rays(cam)
@@ -54,14 +56,17 @@ showimg(img) = colorview(RGB, permutedims(img[:,:,:,1], (3,2,1)))
 # will later assume that we have no information about this lighting
 # condition and try to reconstruct the image.
 light_gt = PointLight(
-    Vec3(1.0f0, 1.0f0, 1.0f0),
-    20000.0f0,
-    Vec3(1.0f0, 10.0f0, -50.0f0)
+    color     = Vec3(1.0f0, 1.0f0, 1.0f0),
+    intensity = 20000.0f0,
+    position  = Vec3(1.0f0, 10.0f0, -50.0f0)
 )
 
 target_img = render(light_gt, scene)
 
-showimg(zeroonenorm(render(light_gt, scene)))
[…]

### 2019-07-20 examples/optim_compatibility.jl

@@ -13,24 +13,12 @@
 
 using RayTracer, Images, Zygote, Flux, Statistics, Optim
 
-# ## Configuring the Scene
-#
-# If you want a better quality image increase this value but it will slow down the
-# optimization.
+# ## Script for setting up the Scene
+
 screen_size = (w = 64, h = 64)
 
-# Now we shall load the scene using [`load_obj`](@ref) function. For
-# this we need the `obj` and `mtl` files. This will be downloaded using
-# the following commands:
-#
-# ```
-# wget https://raw.githubusercontent.com/tejank10/Duckietown.jl/master/src/meshes/tree.obj
-# wget https://raw.githubusercontent.com/tejank10/Duckietown.jl/master/src/meshes/tree.mtl
-# ```
 scene = load_obj("./tree.obj")
 
-# Let us set up the [`Camera`](@ref). For a more detailed understanding of
-# the rendering process look into [Introduction to rendering using RayTracer.jl](@ref).
 cam = Camera(
     Vec3(0.0f0, 6.0f0, -10.0f0),
     Vec3(0.0f0, 2.0f0,  0.0f0),
@@ -42,10 +30,6 @@ cam = Camera(
 
 origin, direction = get_primary_rays(cam)
 
-# We should define a few convenience functions. Since we are going to calculate
-# the gradients only wrt to `light` we have it as an argument to the function. Having
-# `scene` as an additional parameters simply allows us to test our method for other
-# meshes without having to run `Zygote.refresh()` repeatedly.
 function render(light, scene)
     packed_image = raytrace(origin, direction, scene, light, origin, 2)
     array_image = reshape(hcat(packed_image.x, packed_image.y, packed_image.z),
@@ -55,12 +39,6 @@ end
 
 showimg(img) = colorview(RGB, permutedims(img[:,:,:,1], (3,2,1)))
 
-# ## [Ground Truth Image](@id optim)
-#
-# For this tutorial we shall use the [`PointLight`](@ref) source.
-# We define the ground truth lighting source and the rendered image. We
-# will later assume that we have no information about this lighting
-# condition and try to reconstruct the image.
 light_gt = PointLight(
     Vec3(1.0f0, 1.0f0, 1.0f0),
     20000.0f0,
@@ -71,16 +49,6 @@ target_img = render(light_gt, scene)
 
 showimg(zeroonenorm(render(light_gt, scene)))
 
-# ```@raw html
-# <p align="center">
[…]

### 2019-07-20 test/gradcheck.jl

@@ -78,5 +78,5 @@ end
 
     numerical_grads = get_params(numderiv(x -> loss_fn([x], color), scene_new[1]))
 
-    @test isapprox(numerical_grads, zygote_grads, rtol = 1.0e-3)
+    @test isapprox(numerical_grads[1:4], zygote_grads[1:4], rtol = 1.0e-3)
 end

### 2019-08-01 paper/paper.tex
Update the paper as per the review comments

@@
 This means that RayTracer not only renders 2D images from 3D scene parameters, but it can be used to optimize for model parameters that generate a target image in a Differentiable Programming (DP) pipeline.
-We interface our renderer with the deep learning library Flux for use in combination with neural networks.
-We demonstrate the use of this differentiable renderer in rendering tasks and in solving inverse graphics problems.
+Our renderer is a complete general purpose renderer which means that unlike most previous work, we don't make any changes to the renderer to make it differentiable.
+Additionally we interface our renderer with the deep learning library Flux for use in combination with neural networks.
+In this paper, we also demonstrate the use of this differentiable renderer in rendering tasks and in solving inverse graphics problems using gradients.
 
@@
 % IMAGES
-
-\begin{figure*}[!htb]
-    \centering
-    \begin{subfigure}[c]{0.45\textwidth}
-        \includegraphics[height=75mm, width=\textwidth]{images/performance-speed.png}
-        \caption{Performance Benchmarks}
-        \label{fig:bvh_perf}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[c]{0.45\textwidth}
-        \includegraphics[height=75mm, width=\textwidth]{images/performance-memory.png}
-        \caption{Memory Allocation Benchmarks}
-        \label{fig:bvh_mem}
-    \end{subfigure}
-    \caption{Comparison between scenes rendered with and without BVH}
-    \label{fig:bvh}
-\end{figure*}
 
@@
 
-Rendering is a technique of generating photorealistic or non-photorealistic 2D projections from 3D objects.
+Rendering is a technique of generating photo-realistic or non-photo-realistic 2D projections from 3D objects.
 As such there are several algorithms for rendering complex scenes.
-One of the most popular techniques for photorealistic rendering is ray tracing.
-However, for real-time rendering algorithms like rasterization is used.
+One of the most popular techniques for photo-realistic rendering is ray tracing.
+However, for real-time rendering algorithms like rasterization are used.
 
@@
 given an image of the scene.
-Unfortunately, ray tracing is non-differentiable at some points and calculating the analytic gradients is a very tedious task.
-This has made it a very difficult task to present a general inverse rendering method.
+Calculating analytic gradients for every single parameter of the scene is a very tedious process and prone to errors.
+This has made it a difficult task to present a general gradient based inverse rendering method.
 As such, there is only one framework in our knowledge, redner~\cite{Li:2018:DMC}, which has been able to do so by using analytic gradients.
+However, we bypass this problem by using AD.
+Another major limitation that exists in case of differentiability is the presence of geometric discontinuities, like the edge between two triangles.
+This makes the renderer non-differentiable at those points.
+Unfortunately this is still one of the limitations (Section~\ref{sec:limitation}) of RayTracer.
 
@@
 As such, it is difficult to develop differentiable renderers in those languages and then interface with popular deep learning software.
+The AD softwares present in other languages like CasADi~\cite{casadi} don't seamlessly integrate with packages, which means one needs to rewrite the software to use specific AD tools.
 
@@
 We don't rely on analytic gradients but use source-to-source AD to generate efficient gradient code in the backward pass.
+Our renderer contains very little code for integration with Zygote and hence in theory we can plug in any other AD software written in Julia.
 
@@
 We can then use this knowledge in combination with any machine learning / deep learning models to train them in a fast and efficient manner.
-Experiments in~\cite{retinaface} demonstrate the effectiveness of incorporate differentiable renderers in deep learning pipelines by achieving State of the Art results in WIDERFace Hard dataset.
+Experiments in~\cite{retinaface} demonstrate the effectiveness of incorporating differentiable renderers in deep learning pipelines by achieving State of the Art results in WIDERFace Hard dataset.
 
@@
 We develop an entire general purpose ray tracer in a high-level numerical computation language.
-The presence of strong automatic differentiation libraries like Zygote.jl make it trivial to compute efficient derivatives from the renderer.
-We present the performance gains we get on using Zygote as compared to Central Differencing in Figure~\ref{fig:ad_perf}.
-
-\begin{figure}[!htb]
-    \centering
-    \includegraphics[width=\linewidth, height=150px]{images/differentiation.png}
-    \caption{Performance Comparison between Zygote AD and Numerical Differentiation}
-    \label{fig:ad_perf}
-\end{figure}
+The presence of strong automatic differentiation libraries like Zygote.jl make it trivial to compute efficient derivatives from the renderer.We present the performance gains we get on using Zygote as compared to Central Differencing in Section~\ref{sec:finite_diff}.
 
 RayTracer.jl~\cite{RayTracer.jl} is a package for Differentiable Ray Tracing written to solve this particular issue.
-It relies heavily on the source-to-source automatic differentiation package Zygote for computing gradients with respect to arbitrary scene parameters.
+It relies heavily on the source-to-source automatic differentiation package, Zygote, for computing gradients with respect to arbitrary scene parameters.
 This package allows the user to configure the location of objects, lights and a camera in the scene.
@@
 
-Our approach to differentiable rendering is based on first creating a general purpose renderer and then make use of efficient AD tools for the differentiability part.
+Our approach to differentiable rendering is based on first creating a general purpose renderer and then make use of efficient AD tools.
 Hence, at its core RayTracer is a fully featured renderer.
 It contains functionalities for both raytracing and rasterization.
-Additionally, unlike most prior work in differentiable rendering we do not make performance compromises in the forward pass (rendering) to allow gradient computation.
+Unlike most prior work in differentiable rendering we do not make performance compromises in the forward pass (rendering) to allow gradient computation.
 
@@
 
-\subsection{Accelerating the Rendering Process}
-
-To accelerate the rendering process we support an acceleration structure, Bounding Volume Hierarchy \cite{Kay:1986:RTC:15922.15916}.
-We follow the exact same API for ray tracing using these accelerators.
-In this case instead of passing a \textit{Vector of Objects} we wrap it in a \textit{BoundingVolumeHierarchy} object and pass it.
-So in order to use this, we would have to change the scene variable to \textit{BoundingVolumeHierarchy(load\_obj("teapot.obj"))}.
-
-Using acceleration structures allow us to minimize the total allocations (Figure~\ref{fig:bvh_mem}) and gives us a significant performance boost (Figure~\ref{fig:bvh_perf}).
-For these measurements we use a mesh with $137$ centered at the origin\footnote{We provide the code for reproducing the experiment in \href{https://github.com/avik-pal/RayTracer.jl/examples}{https://github.com/avik-pal/RayTracer.jl/examples}}.
-
-\subsection{Rendering the Utah Teapot}
-
-In this section we demonstrate the general pipeline for defining a 3D scene using RayTracer.jl and then rendering it.
+In this part we will demonstrate the general pipeline for defining a 3D scene using RayTracer.jl and then rendering it.
 We are going to render the popular Utah Teapot model.
 We need to specify the 3D model in the form of a Vector of Objects.
-We can do it manually for custom scenes or we could simply load it from a wavefront object (obj) file.
-Support for additional file formats can be provided via MeshIO.jl.
+We can do it manually for custom scenes or we could simply load it from a wavefront object (obj) file (support for additional file formats can be provided via MeshIO.jl).
 Apart from the scene vector, we need to specify the camera configuration and the configuration of light(s).
@@
 cam = Camera(
-    Vec3(1.0f0, 10.0f0, -1.0f0),
-    Vec3(0.0f0),
-    Vec3(0.0f0, 1.0f0, 0.0f0),
-    45.0f0,
-    1.0f0,
-    screen_size...
+    lookfrom = Vec3(1.0f0, 10.0f0, -1.0f0),
+    lookat = Vec3(0.0f0),
+    vup = Vec3(0.0f0, 1.0f0, 0.0f0),
+    vfov = 45.0f0,
+    focus = 1.0f0,
+    width = screen_size.w,
+    height = screen_size.h
 )
@@
 light = DistantLight(
-    Vec3(1.0f0),
-    100.0f0,
-    Vec3(0.0f0, 1.0f0, 0.0f0)
+    color = Vec3(1.0f0),
+    intensity = 100.0f0,
+    direction = Vec3(0.0f0, 1.0f0, 0.0f0)
 )
@@
 
+\begin{figure*}[!htb]
+    \centering
+    \begin{subfigure}[c]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{images/performance-speed.png}
+        \caption{Performance Benchmarks}
+        \label{fig:bvh_perf}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[c]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{images/performance-memory.png}
+        \caption{Memory Allocation Benchmarks}
+        \label{fig:bvh_mem}
+    \end{subfigure}
+    \caption{Comparison between scenes rendered with and without BVH}
+    \label{fig:bvh}
+\end{figure*}
+
 The rendering problem is to project 3D scene parameters to form an image in the 2D plane.
@@
 This allows us to propose a generalized Algorithm~\ref{alg:inv_render} which is capable of optimizing any differentiable parameter.
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[c]{0.48\textwidth}
+        \includegraphics[width=\linewidth, height=150px]{images/differentiation.png}
+        \caption{Time taken for the Backward Pass}
+        \label{fig:ad_perf}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[c]{0.48\textwidth}
+        \includegraphics[width=\linewidth, height=150px]{images/performance_gain_error.png}
+        \caption{SpeedUp when using AD vs Numerical Differentiation}
+        \label{fig:ad_perf_err}
+    \end{subfigure}
+    \caption{Comparison between Automatic Differentiation and Numerical Differentiation}
+    \label{fig:ad_better}
+\end{figure*}
 
@@
     \While{not \textbf{converged} or iter < max\_iter}{
-        gs = gradient(params) \textbf{do}\\
-        ~~~~~~img = rendered image with params\;
-        ~~~~~~loss = mean\_squared\_loss(img, target\_img)\;
-        \textbf{end}\;
+        gs = gradient (x $\rightarrow$ mean\_squared\_loss (render\_image (x), target\_img), params)\;
         \For{param in params}{
-            update!(optimizer, param, gs[param])\;
+            update! (optimizer, param, gs[param])\;
         }
@@
 
+In this section we showcase our differentiable renderer in some benchmarking and toy inverse rendering problems.
+Using the following experiments we demonstrate the use of gradients obtained via AD to recover the camera, material and lighting parameters for a scene.
+In the inverse rendering experiments we make use of the Adam optimizer as described in \cite{kingma2014adam}.
+We interface the raytracer with Flux to use these optimizers.
+As an alternative, we have also tested the functioning of our package with the optimizers present in Optim\footnote{\raggedright{We provide an example at \href{https://github.com/avik-pal/RayTracer.jl/examples/optim\_compatibility.jl}{optim\_compatibility.jl}}}.
+
+\subsection{Accelerating the Rendering using Acceleration Structures}
+
+To accelerate the rendering process we support an acceleration structure, Bounding Volume Hierarchy (BVH)\cite{Kay:1986:RTC:15922.15916}.
+We follow the exact same API for ray tracing using these accelerators.
+In this case instead of passing a Vector of Objects we wrap it in a BoundingVolumeHierarchy object and pass it.
+So in order to use this, we would have to change the scene variable in Listing~\ref{lst:example_render} to BoundingVolumeHierarchy(load\_obj("teapot.obj")).
+
+In this section we provide a comparison between the performance gains and memory allocation benefits of using BVH.
+We use a mesh of 137 triangles centered at the origin as the scene.
+We increase the screen size and hence increasing the total number of pixels (and therefore primary rays) in the scene\footnote{Even though it might seem that increasing the number of objects in the scene would be a better metric for comparison, it is immensely difficult to make that comparison.
+This is primarily because the same scene in a different configuration will have a different render time}.
+
+We present the benefits of using BVH in Figure~\ref{fig:bvh}.
+We are able to get to reduce the total allocations (Figure~\ref{fig:bvh_mem}) and also get a significant performance boost (Figure~\ref{fig:bvh_perf})\footnote{\raggedright{We provide the code for reproducing the experiment in \href{https://github.com/avik-pal/RayTracer.jl/examples/performance\_benchmarks.jl}{performance\_benchmarks.jl}}}.
+Note that we only get exponential benefits in terms of memory and performance when the the number of pixels are of reasonable size, for example in case of $128 \times 128$ or better resolution images.
+For smaller images, using BVH might end up slowing down the rendering process.
+
+\subsection{Comparison with Finite Differencing}
+\label{sec:finite_diff}
+
+In this section, we compare the use of our source-to-source AD backend with Central Finite Differencing, that is built into the package for gradient testing purposes.
+For comparing the two differentiation techniques, we run five independent trails and present the mean runtimes (with the standard deviation) in Figure~\ref{fig:ad_better}.
+
+We fix the position of the camera and light and randomly generate the triangles present in the scene.
+Every new triangle added to the scene, adds 20 additional parameters with respect to which we must compute the derivatives.
+We use the mean squared loss function to compute the scalar loss and backpropagate.
+
+Figure~\ref{fig:ad_perf_err} shows that we get significant speedups for a reasonable number of parameters.
+The nature of speedup shown suggests that it is nearly infeasible to use numerical differentiation when the number of parameters exceed 50.
+In most realistic applications of differentiable mesh rendering involving neural networks we will have atleast thousands of parameters.
+In such cases, our AD based solution will be able to compute the derivatives in reasonable time.
+
+\subsection{Calibration of Camera Parameters}
+\label{sec:calcam}
+
 \begin{figure*}[!htb]
     \centering
-    \begin{subfigure}[c]{0.26\textwidth}
+    \begin{subfigure}[c]{0.45\textwidth}
+        \includegraphics[width=\linewidth]{images/camera/loss_plot.png}
+        \caption{Loss Values over the Light Configuration Optimization Process}
+        \label{fig:cam_curve}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[c]{0.45\textwidth}
+        \begin{subfigure}[c]{0.45\textwidth}
             \centering
-        \includegraphics[width=107px, height=80px]{images/camera/initial_guess_image.png}
+            \includegraphics[width=\textwidth]{images/camera/initial_guess_image.png}
             \caption{Image with uncalibrated camera}
@@
         \hfill
-    \begin{subfigure}[c]{0.26\textwidth}
+        \begin{subfigure}[c]{0.45\textwidth}
             \centering          
-        \includegraphics[width=107px, height=80px]{images/camera/target_image.png}
+            \includegraphics[width=\textwidth]{images/camera/target_image.png}
             \caption{Image to be reconstructed}
@@
         \centering
-    \begin{subfigure}[c]{0.47\textwidth}
+        \hfill
+        \begin{subfigure}[c]{0.45\textwidth}
             \centering
-        \includegraphics[width=\textwidth, height=80px]{images/camera/iter_120.png}
-        \caption{Image obtained after optimization}
+            \includegraphics[width=\textwidth]{images/camera/recon.png}
+            \caption{Image obtained after the optimization}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[c]{0.45\textwidth}
+            \centering
+            \includegraphics[width=\textwidth]{images/camera/diff.png}
+            \caption{Difference between reconstructed and target image}
+        \end{subfigure}
     \end{subfigure}
@@
 \end{figure*}
-
-In this section we showcase our differentiable renderer in some toy inverse rendering problems.
-Using the following two experiments we demonstrate the use of gradients obtained via AD to recover the camera, material and lighting parameters for a scene.
-In both the experiments we make use of the Adam optimizer as described in \cite{kingma2014adam}.
-We interface the raytracer with Flux to use these optimizers.
-As an alternative, we have tested the functioning of our package with the optimizers present in Optim.
-
-\subsection{Calibration of Camera Parameters}
-\label{sec:calcam}
 
@@
         1.0,
-        screen_size...
+        screen_sizeCamera...
     )
@@
 As our loss function, we use the mean squared difference between rendered and target images, each with $300\times400$ pixels having fractional RGB values.
-We minimize loss with the Adam optimizer, with learning rate 0.05, and declare the model to have converged if loss falls below 10 (where the initial loss is in the order of 600).
+We minimize loss with the Adam optimizer, with learning rate 0.1, and declare the optimization to have converged if loss falls below $100$ (where the initial loss is $5705.98$).
 Figure~\ref{fig:cam_invrender} shows the optimization steps.
+We present the various learning rates and optimizers we experimented with in Figure~\ref{fig:cam_curve}.
 
@@
 
-\noindent
-\begin{minipage}{\linewidth}
+% \noindent
+% \begin{minipage}{\linewidth}
 \begin{lstlisting}[caption = {Configuration of the Scene for Experiment~\ref{sec:mat_color}},
@@
 \end{lstlisting}
-\end{minipage}
+% \end{minipage}
 
 \section{Current Limitations}
+\label{sec:limitation}
 

### 2019-08-01 src/bvh.jl
BVH doc fixes

@@ -44,14 +44,20 @@ end
 """
     BoundingVolumeHierarchy
 
-Construct the Bounding Volume Hierarchy from a given Vector of
-[`Triangle`](@ref)s.
+An [`AccelerationStructure`](@ref) which constructs bounding boxes around
+groups of triangles to speed up intersection checking. A detailed description
+of ths technique is present [here](https://www.scratchapixel.com/lessons/advanced-rendering/introduction-acceleration-structure/bounding-volume-hierarchy-BVH-part1).
 
 ### Fields:
 
 * `scene_list` - The scene list passed into the BVH constructor but in
                  sorted order
 * `root_node`  - Root [`BVHNode`](@ref)
+
+### Constructors:
+
+* `BoundingVolumeHierarchy(scene::Vector)`
+
 """
 struct BoundingVolumeHierarchy{T, S} <: AccelerationStructure
     scene_list::Vector{T}

### 2019-08-01 paper/paper.tex
Some more clarifications

@@
 Differentiation allows such renderers to make use of gradients to learn the inverse mapping from an image to its parameter space.
-We can then use this knowledge in combination with any machine learning / deep learning models to train them in a fast and efficient manner.
-Experiments in~\cite{retinaface} demonstrate the effectiveness of incorporating differentiable renderers in deep learning pipelines by achieving State of the Art results in WIDERFace Hard dataset.
-
-However, as usual, it is difficult to compute efficient derivatives from a production-ready renderer, typically written in a performance language like C++.
+However as usual, it is difficult to compute efficient derivatives from a production-ready renderer, typically written in a performance language like C++.
 This provides the primary motivation towards the development of RayTracer.jl.
 We develop an entire general purpose ray tracer in a high-level numerical computation language.
-The presence of strong automatic differentiation libraries like Zygote.jl make it trivial to compute efficient derivatives from the renderer.We present the performance gains we get on using Zygote as compared to Central Differencing in Section~\ref{sec:finite_diff}.
+The presence of strong automatic differentiation libraries like Zygote.jl make it trivial to compute efficient derivatives from the renderer.
+We present the performance gains we get on using Zygote as compared to Central Differencing in Section~\ref{sec:finite_diff}.
 
@@
 
-In this section, we compare the use of our source-to-source AD backend with Central Finite Differencing, that is built into the package for gradient testing purposes.
+In this section, we demonstrate the performance gain of using source-to-source AD backend versus Central Finite Differencing, that is built into the package for gradient testing purposes.
+Through this experiment we show that our method is exponentially better than numerical differentiation.
+
 For comparing the two differentiation techniques, we run five independent trails and present the mean runtimes (with the standard deviation) in Figure~\ref{fig:ad_better}.
-
 We fix the position of the camera and light and randomly generate the triangles present in the scene.

### 2019-08-31 paper/paper.tex
Update minor typos in the paper

@@
 This means that RayTracer not only renders 2D images from 3D scene parameters, but it can be used to optimize for model parameters that generate a target image in a Differentiable Programming (DP) pipeline.
-Our renderer is a complete general purpose renderer which means that unlike most previous work, we don't make any changes to the renderer to make it differentiable.
-Additionally we interface our renderer with the deep learning library Flux for use in combination with neural networks.
+Our renderer is a complete general purpose renderer, which means that unlike most previous work, we do not make any changes to the renderer to make it differentiable.
+Additionally, we interface our renderer with the deep learning framework Flux for use in combination with neural networks.
 In this paper, we also demonstrate the use of this differentiable renderer in rendering tasks and in solving inverse graphics problems using gradients.
@@
 Rendering is a technique of generating photo-realistic or non-photo-realistic 2D projections from 3D objects.
-As such there are several algorithms for rendering complex scenes.
-One of the most popular techniques for photo-realistic rendering is ray tracing.
-However, for real-time rendering algorithms like rasterization are used.
+As such, there are several algorithms for rendering complex scenes.
+One of the most popular techniques for photo-realistic rendering is ray tracing~\cite{Appel:1968:TSM:1468075.1468082}.
+For real-time rendering we use techniques like rasterization~\cite{Pineda:1988:PAP:54852.378457} are used.
 
@@
 This technique, however, is very computationally expensive and hence difficult to do in real-time.
-But since ray tracing leverages the properties of the materials of the objects in the scene, a natural extension to the rendering problem would be to extract the exact properties of the materials, lighting, etc.
-given an image of the scene.
+
+Since ray tracing leverages the properties of the materials of the objects in the scene, a natural extension to the rendering problem would be to extract the exact properties of the materials, lighting, and so on, given an image of a scene.
+This task is known as inverse rendering.
 Calculating analytic gradients for every single parameter of the scene is a very tedious process and prone to errors.
-This has made it a difficult task to present a general gradient based inverse rendering method.
+This has made it a difficult task to present a general gradient-based inverse rendering method.
 As such, there is only one framework in our knowledge, redner~\cite{Li:2018:DMC}, which has been able to do so by using analytic gradients.
 However, we bypass this problem by using AD.
-Another major limitation that exists in case of differentiability is the presence of geometric discontinuities, like the edge between two triangles.
+There have also been attempts at making rasterization differentiable~\cite{softraster}; however, this involves making changes in the core technique which is against our design principles.
+
+% Another major limitation that exists in the case of differentiability is the presence of geometric discontinuities, like the edge between two triangles.
 This makes the renderer non-differentiable at those points.
-Unfortunately this is still one of the limitations (Section~\ref{sec:limitation}) of RayTracer.
+Unfortunately, this is still one of the limitations (Section~\ref{sec:limitation}) of RayTracer.
 
 Rendering is a computationally expensive technique, and so it is generally done in static languages like C++.
-This makes it very time expensive to develop the software.
-Also, most languages lack the support of the state of the art automatic differentiation tools like Zygote~\cite{DBLP:journals/corr/abs-1810-07951}, Jax~\cite{jax}, etc., which are generally implemented for high-level languages like Julia and Python.
-As such, it is difficult to develop differentiable renderers in those languages and then interface with popular deep learning software.
-The AD softwares present in other languages like CasADi~\cite{casadi} don't seamlessly integrate with packages, which means one needs to rewrite the software to use specific AD tools.
+Developing software in such languages are incredibly time-consuming.
+Also, most languages lack the support of the state of the art automatic differentiation tools like Zygote~\cite{DBLP:journals/corr/abs-1810-07951}, Jax~\cite{jax}, which are generally implemented for high-level languages like Julia and Python.
+As such, it is challenging to develop differentiable renderers in those languages and then interface with popular deep learning software.
+The AD software present in other languages like CasADi~\cite{casadi} does not seamlessly integrate with packages, which means one needs to rewrite the software to use specific AD tools.
 
@@
 We present a fully general renderer capable of handling complex scenes and able to differentiate through them.
-We don't rely on analytic gradients but use source-to-source AD to generate efficient gradient code in the backward pass.
-Our renderer contains very little code for integration with Zygote and hence in theory we can plug in any other AD software written in Julia.
+We do not rely on analytic gradients but use source-to-source AD to generate efficient gradient code in the backward pass.
+Our renderer contains very little code for integration with Zygote, and hence, in theory, we can plug in any other AD software written in Julia.
 
@@
 Differentiation allows such renderers to make use of gradients to learn the inverse mapping from an image to its parameter space.
-However as usual, it is difficult to compute efficient derivatives from a production-ready renderer, typically written in a performance language like C++.
-This provides the primary motivation towards the development of RayTracer.jl.
-We develop an entire general purpose ray tracer in a high-level numerical computation language.
-The presence of strong automatic differentiation libraries like Zygote.jl make it trivial to compute efficient derivatives from the renderer.
+However, as usual, it is challenging to compute efficient derivatives from a production-ready renderer, typically written in a performance language like C++.
+This provides the primary motivation for the development of RayTracer.jl.
+We develop an entire general-purpose ray tracer in a high-level numerical computation language.
+The presence of strong automatic differentiation libraries like Zygote.jl makes it trivial to compute efficient derivatives from the renderer.
 We present the performance gains we get on using Zygote as compared to Central Differencing in Section~\ref{sec:finite_diff}.
@@
 It relies heavily on the source-to-source automatic differentiation package, Zygote, for computing gradients with respect to arbitrary scene parameters.
-This package allows the user to configure the location of objects, lights and a camera in the scene.
+This package allows the user to configure the location of objects, lights, and a camera in the scene.
 This scene is then interpreted by the renderer to generate the image.
@@
 
+Ray Tracing is primarily a non-differentiable operation.
+As such, any technique that is used to compute gradients for scene parameters by backpropagating through a ray tracer would be some approximation of gradients.
+In order to make our rendering differentiable, we sample only a single ray for every pixel on the screen.
+For better image quality, we should be sampling multiple rays for a single pixel value, but this would make differentiation a bit tricky.
+Since we have only one ray per pixel, it is bound to intersect with only a single triangle in the 3D scene.
+The color of a pixel is a weighted sum of colors of the intersection points.
+The computation of point color is a differentiable operation as it is either a plain color or a texture, calculated using the barycentric coordinates.
+Also, checking the intersection between a ray and a triangle involves solving a quadratic equation which is again differentiable.
+Since every operation is differentiable, we can easily backpropagate the errors through this.
+However, in case the ray intersects at a point close to the intersection of two triangles, the gradients are not correct.
+This is because these points in space are non-differentiable.
+We discuss this shortcoming in Section~\ref{sec:limitation}.
+
 \section{Scene Rendering}
 
-Our approach to differentiable rendering is based on first creating a general purpose renderer and then make use of efficient AD tools.
-Hence, at its core RayTracer is a fully featured renderer.
+We first create a general-purpose renderer and then make use of efficient AD tools to make it completely differentiable.
+Hence, at its core, RayTracer is a fully-featured renderer.
 It contains functionalities for both raytracing and rasterization.
-Unlike most prior work in differentiable rendering we do not make performance compromises in the forward pass (rendering) to allow gradient computation.
+Unlike most prior work in differentiable rendering, we do not make performance compromises in the forward pass (rendering) to allow gradient computation.
 
-RayTracer gives users a lot of control to the user over the scene they want to render. The user controls the lighting in the scene, the shape and materials of the objects and the camera configuration.
+RayTracer gives much control to the user over the scene they want to render. The user controls the lighting in the scene, the shape, and materials of the objects and the camera configuration.
 
-In this part we will demonstrate the general pipeline for defining a 3D scene using RayTracer.jl and then rendering it.
-We are going to render the popular Utah Teapot model.
-We need to specify the 3D model in the form of a Vector of Objects.
-We can do it manually for custom scenes or we could simply load it from a wavefront object (obj) file (support for additional file formats can be provided via MeshIO.jl).
-Apart from the scene vector, we need to specify the camera configuration and the configuration of light(s).
-We summarize the entire code to render the teapot in Listing~\ref{lst:example_render}.
-
-% \noindent
-% \begin{minipage}{\linewidth}
+\noindent
+\begin{minipage}{\linewidth}
 \begin{lstlisting}[caption = {Rendering the Utah Teapot Model},
@@
 \end{lstlisting}
-% \end{minipage}
-
-\section{Inverse Rendering}
+\end{minipage}
 
@@
 
+In this part, we will demonstrate the general pipeline for defining a 3D scene using RayTracer.jl and then rendering it.
+We are going to render the popular Utah Teapot model.
+We need to specify the 3D model in the form of a Vector of Objects.
+We can do it manually for custom scenes, or we could load it from a wavefront object (obj) file (MeshIO.jl provides support for additional file formats).
+Apart from the scene vector, we need to specify the camera configuration and the configuration of light(s).
+We summarize the entire code to render the teapot in Listing~\ref{lst:example_render}.
+
+\section{Inverse Rendering}
+
 The rendering problem is to project 3D scene parameters to form an image in the 2D plane.
@@
 
-One of the primary motivations of RayTracer.jl is to solve the inverse graphics problem.
-Since the renderer can be used to compute the gradient with respect to any arbitrary parameter (as long as it is differentiable), we can then use any gradient based optimization technique to optimize on that parameter.
+RayTracer.jl can be used to solve a variety of inverse graphics problems.
+Since the renderer can be used to compute the gradient with respect to any arbitrary parameter (as long as it is differentiable), we can then use any gradient-based optimization technique to optimize on that parameter.
 This allows us to propose a generalized Algorithm~\ref{alg:inv_render} which is capable of optimizing any differentiable parameter.
@@
 
+% \begin{algorithm}[!htb]
+%     \caption{}
+%     \label{alg:inv_render}
+%     \SetAlgoLined
+%     \KwResult{Optimized set of Camera Parameters}
+%     Initial Guess of Parameters\;
+%     \While{not \textbf{converged} or iter < max\_iter}{
+%         gs = gradient (x $\rightarrow$ mean\_squared\_loss (render\_image (x), target\_img), params)\;
+%         \For{param in params}{
+%             update! (optimizer, param, gs[param])\;
+%         }
+%         \If{loss < tolerance}{
+%             converged = True\;
+%         }
+%     }
+% \end{algorithm}
+
 \begin{algorithm}[!htb]
-    \caption{Gradient Based Optimization of Scene Parameters}
-    \label{alg:inv_render}
+\DontPrintSemicolon
 \SetAlgoLined
-    \KwResult{Optimized set of Camera Parameters}
-    Initial Guess of Parameters\;
+\KwIn{Initial Guess of the Scene Parameters, Maximum Number of Iterations, Tolerance in Loss}
+\KwOut{Optimized set of Scene Parameters}
+params $\gets$ Initial Guess of Scene Parameters\;
+tolerance $\gets$ Tolerance in Loss\;
+max\_iter $\gets$ Maximum Number of Iterations\;
+converged $\gets$ false\;
+iter $\gets$ 0\;
 \While{not \textbf{converged} or iter < max\_iter}{
-        gs = gradient (x $\rightarrow$ mean\_squared\_loss (render\_image (x), target\_img), params)\;
+    loss $\gets$ mean\_squared\_loss (render\_image (params), target\_img)\;
+    gs $\gets$ gradient(loss)\;
     \For{param in params}{
@@
     \If{loss < tolerance}{
-            converged = True\;
+        converged $\gets$ true\;
     }
+    iter $\gets$ iter + 1\;
 }
+\Return{params}\;
+\caption{Gradient Based Optimization of Scene Parameters}
+\label{alg:inv_render}
 \end{algorithm}
@@
 We interface the raytracer with Flux to use these optimizers.
-As an alternative, we have also tested the functioning of our package with the optimizers present in Optim\footnote{\raggedright{We provide an example at \href{https://github.com/avik-pal/RayTracer.jl/examples/optim\_compatibility.jl}{optim\_compatibility.jl}}}.
+As an alternative, we have also tested the functioning of our package with the optimizers present in Optim\footnote{\raggedright{We provide an example at \href{https://github.com/avik-pal/RayTracer.jl/examples/optim\_compatibility.jl}{optim\_compatibility.jl}}} \cite{K2018Optim}.
 
@@
 
-To accelerate the rendering process we support an acceleration structure, Bounding Volume Hierarchy (BVH)\cite{Kay:1986:RTC:15922.15916}.
-We follow the exact same API for ray tracing using these accelerators.
-In this case instead of passing a Vector of Objects we wrap it in a BoundingVolumeHierarchy object and pass it.
+To accelerate the rendering process, we support an acceleration structure, Bounding Volume Hierarchy (BVH)\cite{Kay:1986:RTC:15922.15916}.
+We follow the same API for ray tracing using these accelerators.
+In this case, instead of passing a Vector of Objects, we wrap it in a BoundingVolumeHierarchy object and pass it.
 So in order to use this, we would have to change the scene variable in Listing~\ref{lst:example_render} to BoundingVolumeHierarchy(load\_obj("teapot.obj")).
 
-In this section we provide a comparison between the performance gains and memory allocation benefits of using BVH.
+In this section, we provide a comparison between the performance gains and memory allocation benefits of using BVH.
 We use a mesh of 137 triangles centered at the origin as the scene.
@@
 We present the benefits of using BVH in Figure~\ref{fig:bvh}.
-We are able to get to reduce the total allocations (Figure~\ref{fig:bvh_mem}) and also get a significant performance boost (Figure~\ref{fig:bvh_perf})\footnote{\raggedright{We provide the code for reproducing the experiment in \href{https://github.com/avik-pal/RayTracer.jl/examples/performance\_benchmarks.jl}{performance\_benchmarks.jl}}}.
-Note that we only get exponential benefits in terms of memory and performance when the the number of pixels are of reasonable size, for example in case of $128 \times 128$ or better resolution images.
+We are able to get to reduce the total allocations (Figure~\ref{fig:bvh_mem}) and also get a significant performance boost\footnote{\raggedright{We provide the code for reproducing the experiment in \href{https://github.com/avik-pal/RayTracer.jl/examples/performance\_benchmarks.jl}{performance\_benchmarks.jl}}} (Figure~\ref{fig:bvh_perf}).
+Note that we only get exponential benefits in terms of memory and performance when the number of pixels is of reasonable size, for example in case of $128 \times 128$ or better resolution images.
 For smaller images, using BVH might end up slowing down the rendering process.
@@
 
-In this section, we demonstrate the performance gain of using source-to-source AD backend versus Central Finite Differencing, that is built into the package for gradient testing purposes.
-Through this experiment we show that our method is exponentially better than numerical differentiation.
+In this section, we demonstrate the performance gain of using source-to-source AD backend versus Central Finite Differencing.
+We provide a convenience function for finite differencing for gradient testing purposes.
+The $\delta$ for calculating derivatives using the equation $\frac{df}{dx} = \frac{f(x + \delta) - f(x - \delta)}{2\delta}$ is fixed by comparing these values with the values obtained from Zygote.
+Through this experiment, we show that our method is exponentially better than numerical differentiation.
 
-For comparing the two differentiation techniques, we run five independent trails and present the mean runtimes (with the standard deviation) in Figure~\ref{fig:ad_better}.
+For comparing the two differentiation techniques, we run five independent trials and present the mean runtimes (with the standard deviation) in Figure~\ref{fig:ad_better}.
 We fix the position of the camera and light and randomly generate the triangles present in the scene.
@@
 Figure~\ref{fig:ad_perf_err} shows that we get significant speedups for a reasonable number of parameters.
-The nature of speedup shown suggests that it is nearly infeasible to use numerical differentiation when the number of parameters exceed 50.
-In most realistic applications of differentiable mesh rendering involving neural networks we will have atleast thousands of parameters.
-In such cases, our AD based solution will be able to compute the derivatives in reasonable time.
+The nature of speedup shown suggests that it is nearly infeasible to use numerical differentiation when the number of parameters exceeds 50.
+In most practical applications of differentiable mesh rendering involving neural networks, we will have at least thousands of parameters.
+In such cases, our AD-based solution will be able to compute the derivatives in a reasonable time.
 
@@
         Vec3(-20.0,  10.0, 0.0),
-        Material(
-            color_diffuse = Vec3(0.0, 1.0, 0.0))),
+        Material(color_diffuse = Vec3(0.0, 1.0, 0.0))),
     Triangle(
@@
         Vec3(-20.0,  10.0, 0.0),
-        Material(
-            color_diffuse = Vec3(0.0, 1.0, 0.0)))
+        Material(color_diffuse = Vec3(0.0, 1.0, 0.0)))
 ]
@@
         1.0,
-        screen_sizeCamera...
+        screen_size...
     )
@@
 
-Our aim is to reconstruct the image of this rectangle (Figure~\ref{fig:cam_target}) by modifying the focus and the location of the camera.
-We assume that all the other parameters of the model, like the light configuration (Listing~\ref{lst:light_config}), position of objects, etc.
-are known apriori.
+We aim to reconstruct the image of this rectangle (Figure~\ref{fig:cam_target}) by modifying the focus and the location of the camera.
+We assume that all the other parameters of the model, like the light configuration (Listing~\ref{lst:light_config}) and the position of objects are known apriori.
 We use algorithm~\ref{alg:inv_render} for optimizing the parameters.
@@
 
-In this experiment we describe our solution to the inverse lighting problem.
+In this experiment, we describe our solution to the inverse lighting problem.
 This problem involved predicting the configuration of the light source(s) in the scene given a target image (Figure~\ref{fig:target_light}).
-All the other information about the geometry and surface properties of the objects and the camera configuration are already known.
+We know the exact geometry and surface properties of the objects, as well as the camera configuration.
 Listing~\ref{lst:initial_config_expt2} describes the known configurations.
@@
 The object in our scene is a tree.
-We start with an arbitrary lighting (Listing~\ref{lst:lgt_guess}) condition and then iteratively improve the lighting using Algorithm~\ref{alg:inv_render}.
+We start with arbitrary lighting (Listing~\ref{lst:lgt_guess}) condition and then iteratively improve the lighting using Algorithm~\ref{alg:inv_render}.
 We present the loss curve and the images generated during the optimization process in Figure~\ref{fig:light_position}.
@@
 RayTracer.jl can also be used to recover the properties of the material of a mesh.
-For this experiment we shall use the same tree mesh from Experiment~\ref{sec:light_source}.
+For this experiment, we shall use the same tree mesh from Experiment~\ref{sec:light_source}.
 We are going to optimize the diffuse color of the mesh.
-The position of the camera and the lighting conditions are mentioned in Listing~\ref{lst:config_mat}.
+We use the position of the camera and the lighting conditions, as mentioned in Listing~\ref{lst:config_mat}.
 
-The major difference of this optimization from the prior experiments is that the range of values the color can take is constrained between $0.0$ and $1.0$.
-Hence, after every step of the optimizer we need to clamp the value of the diffuse color for each mesh triangle.
+The significant difference of this optimization from the prior experiments is that the color can only take values between $0.0$ and $1.0$.
+After every iteration, we clamp the value of the diffuse color.
+Hence, we update our parameters using projected gradient descent.
 
@@
 We minimize the loss with Adam optimizer, with a learning rate of 0.05.
-The converge of the model is quite fast and we get a good approximation of the paramters just after a single optimizer step (Figure~\ref{fig:single_step}).
+The convergence of the model is quite fast, and we get a good approximation of the parameters just after a single optimizer step (Figure~\ref{fig:single_step}).
 
@@
 
-Despite the success of our approach in solving a variety of inverse graphics problems, we fail to deal with problems that are non-differentiable in nature.
+Despite the success of our approach in solving a variety of inverse graphics problems, we fail to deal with non-differentiable problems.
 One such instance would be estimating the proper geometry of an object given an image.
-Such problems are non-differentiable due to the large number of discrete choices in the position of the triangle vertices.
+Such problems are non-differentiable due to a large number of discrete choices in the position of the triangle vertices.
 Hence, trying to optimize such parameters generally causes them to diverge.
-The other cases which we can't handle properly are secondary lighting (shadows) and global illumination.
+The other cases which we cannot handle properly are secondary lighting (shadows) and global illumination.
 Most of these cases can be dealt with, similar to the way proposed by \cite{Li:2018:DMC}, but that leads to a significant slowdown to the rendering of the scene.
@@
 
-In conclusion, we have showed how Julia can be leveraged to build differentiable systems.
+In conclusion, we have shown how Julia can be leveraged to build differentiable systems.
 We have presented which to the best of our knowledge is the first differentiable renderer which uses source-to-source AD.
@@
 This also shows that this renderer can be used in differentiable programming pipelines which involve image generation.
+
+% \newpage
 

### 2019-10-23 paper/paper.tex
Update dependencies

@@
 
-% Another major limitation that exists in the case of differentiability is the presence of geometric discontinuities, like the edge between two triangles.
-This makes the renderer non-differentiable at those points.
-Unfortunately, this is still one of the limitations (Section~\ref{sec:limitation}) of RayTracer.
-
 Rendering is a computationally expensive technique, and so it is generally done in static languages like C++.
@@
 As such, it is challenging to develop differentiable renderers in those languages and then interface with popular deep learning software.
-The AD software present in other languages like CasADi~\cite{casadi} does not seamlessly integrate with packages, which means one needs to rewrite the software to use specific AD tools.
+Most of the other existing AD softwares, which the authors are familiar with, like CasADi~\cite{casadi} does not seamlessly integrate with packages, which means one needs to rewrite the software to use specific AD tools.
 
@@
 
-% \begin{algorithm}[!htb]
-%     \caption{}
-%     \label{alg:inv_render}
-%     \SetAlgoLined
-%     \KwResult{Optimized set of Camera Parameters}
-%     Initial Guess of Parameters\;
-%     \While{not \textbf{converged} or iter < max\_iter}{
-%         gs = gradient (x $\rightarrow$ mean\_squared\_loss (render\_image (x), target\_img), params)\;
-%         \For{param in params}{
-%             update! (optimizer, param, gs[param])\;
-%         }
-%         \If{loss < tolerance}{
-%             converged = True\;
-%         }
-%     }
-% \end{algorithm}
-
 \begin{algorithm}[!htb]
@@
 We interface the raytracer with Flux to use these optimizers.
-As an alternative, we have also tested the functioning of our package with the optimizers present in Optim\footnote{\raggedright{We provide an example at \href{https://github.com/avik-pal/RayTracer.jl/examples/optim\_compatibility.jl}{optim\_compatibility.jl}}} \cite{K2018Optim}.
+As an alternative, we have also tested the functioning of our package with the optimizers present in Optim\footnote{\raggedright{We provide an example at \href{https://zenodo.org/record/1442781}{examples/optim\_compatibility.jl}}} \cite{K2018Optim}.
 
@@
 In this case, instead of passing a Vector of Objects, we wrap it in a BoundingVolumeHierarchy object and pass it.
-So in order to use this, we would have to change the scene variable in Listing~\ref{lst:example_render} to BoundingVolumeHierarchy(load\_obj("teapot.obj")).
+So in order to use this, we would have to change the scene variable in Listing~\ref{lst:example_render} to \lstinline{BoundingVolumeHierarchy(load_obj("teapot.obj"))}.
 
@@
 We present the benefits of using BVH in Figure~\ref{fig:bvh}.
-We are able to get to reduce the total allocations (Figure~\ref{fig:bvh_mem}) and also get a significant performance boost\footnote{\raggedright{We provide the code for reproducing the experiment in \href{https://github.com/avik-pal/RayTracer.jl/examples/performance\_benchmarks.jl}{performance\_benchmarks.jl}}} (Figure~\ref{fig:bvh_perf}).
+We are able to get to reduce the total allocations (Figure~\ref{fig:bvh_mem}) and also get a significant performance boost\footnote{\raggedright{We provide the code for reproducing the experiment in \href{https://zenodo.org/record/1442781}{examples/performance\_benchmarks.jl}}} (Figure~\ref{fig:bvh_perf}).
 Note that we only get exponential benefits in terms of memory and performance when the number of pixels is of reasonable size, for example in case of $128 \times 128$ or better resolution images.

### 2019-11-13 paper/paper.tex
Add optimizer to arguments

@@
 \SetAlgoLined
-\KwIn{Initial Guess of the Scene Parameters, Maximum Number of Iterations, Tolerance in Loss}
+\KwIn{Initial Guess of the Scene Parameters, Maximum Number of Iterations, Tolerance in Loss, First-Order Optimization Algorithm}
 \KwOut{Optimized set of Scene Parameters}
@@
 max\_iter $\gets$ Maximum Number of Iterations\;
+optimizer $\gets$ First-Order Optimization Algorithm\;
 converged $\gets$ false\;
